### 2024-04-22 literature/BertModel.tex
Add files via upload
literature for choosing Bert Model

\documentclass{article}
\begin{document}
Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks. However, pre-trained language models are usually computationally expensive, so it is difficult to efficiently execute them on resource-restricted devices. To accelerate inference and reduce model size while maintaining accuracy, we first propose a novel Transformer distillation method that is specially designed for knowledge distillation (KD) of the Transformer-based models. By leveraging this new KD method, the plenty of knowledge encoded in a large teacher BERT can be effectively transferred to a small student Tiny-BERT. Then, we introduce a new two-stage learning framework for TinyBERT, which performs Transformer distillation at both the pretraining and task-specific learning stages. This framework ensures that TinyBERT can capture he general-domain as well as the task-specific knowledge in BERT.
TinyBERT with 4 layers is empirically effective and achieves more than 96.8\% the performance of its teacher BERTBASE on GLUE benchmark, while being 7.5x smaller and 9.4x faster on inference. TinyBERT with 4 layers is also significantly better than 4-layer state-of-the-art baselines on BERT distillation, with only about 28\% parameters and about 31\% inference time of them. Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.

Source: https://arxiv.org/abs/1909.10351

\end{document}

### 2024-04-22 paper/paper-part2.tex
refactor literature search for #3

--- 2024-04-22 literature/BertModel.tex
@@
-\documentclass{article}
-\begin{document}
-Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks.
+\section{Related Work}
+
+Why have we choosen model X and model Y for our work?
+
+From~\cite{jiao20}: Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks.
 However, pre-trained language models are usually computationally expensive, so it is difficult to efficiently execute them on resource-restricted devices.
@@
 Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.
-
-Source: https://arxiv.org/abs/1909.10351
-
-\end{document}

### 2024-04-22 paper/paper.tex
refactor literature search for #3

%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
% twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
\usepackage{listings}
%% auto break lines
\lstset{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2022}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{Woodstock'22: Symposium on the irreproducible science,
  June 07--11, 2022, Woodstock, NY}

%%
%% The "title" command
\title{A better way to format your document for CEUR-WS}

\tnotemark[1]
\tnotetext[1]{You can use this document as the template for preparing your
  publication. We recommend using the latest version of the ceurart style.}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1,2]{Dmitry S. Kulyabov}[%
orcid=0000-0002-0877-7063,
email=kulyabov-ds@rudn.ru,
url=https://yamadharma.github.io/,
]
\cormark[1]
\fnmark[1]
\address[1]{Peoples' Friendship University of Russia (RUDN University),
  6 Miklukho-Maklaya St, Moscow, 117198, Russian Federation}
\address[2]{Joint Institute for Nuclear Research,
  6 Joliot-Curie, Dubna, Moscow region, 141980, Russian Federation}

\author[3]{Ilaria Tiddi}[%
orcid=0000-0001-7116-9338,
email=i.tiddi@vu.nl,
url=https://kmitd.github.io/ilaria/,
]
\fnmark[1]
\address[3]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}

\author[4]{Manfred Jeusfeld}[%
orcid=0000-0002-9421-8566,
email=Manfred.Jeusfeld@acm.org,
url=http://conceptbase.sourceforge.net/mjf/,
]
\fnmark[1]
\address[4]{University of Skövde, Högskolevägen 1, 541 28 Skövde, Sweden}

%% Footnotes
\cortext[1]{Corresponding author.}
\fntext[1]{These authors contributed equally.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX{} document is presented as an
  article formatted for publication by CEUR-WS in a conference
  proceedings. Based on the ``ceurart'' document class, this article
  presents and explains many of the common variations, as well as many
  of the formatting elements an author may use in the preparation of
  the documentation of their work.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  LaTeX class \sep
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

CEUR-WS's article template provides a consistent \LaTeX{} style for
use across CEUR-WS publications, and incorporates accessibility and
metadata-extraction functionality. This document will explain the
major features of the document class.

If you are new to publishing with CEUR-WS, this document is a valuable
guide to the process of preparing your work for publication.

\input{paper-part2}

The ``\verb|ceurart|'' document class can be used to prepare articles
for any CEUR-WS publication, and for any stage of publication, from
review to final ``camera-ready'' copy with {\itshape very} few changes
to the source.

This class depends on the following packages
for its proper functioning:

\begin{itemize}
\item \verb|natbib.sty| for citation processing;
\item \verb|geometry.sty| for margin settings;
\item \verb|graphicx.sty| for graphics inclusion;
\item \verb|hyperref.sty| optional package if hyperlinking is required in
  the document;
\item \verb|fontawesome5.sty| optional package for bells and whistles.
\end{itemize}

All the above packages are part of any
standard \LaTeX{} installation.
Therefore, the users need not be
bothered about downloading any extra packages.

\section{Modifications}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \verb|\vspace| command to manually adjust the
vertical spacing between elements of your work --- is not allowed.

\section{Template parameters}

There are a number of template
parameters which modify some part of the \verb|ceurart| document class.
This parameters are enclosed in square
brackets and are a part of the \verb|\documentclass| command:
\begin{lstlisting}
  \documentclass[parameter]{ceurart}
\end{lstlisting}

Frequently-used parameters, or combinations of parameters, include:
\begin{itemize}
\item \verb|twocolumn| : Two column layout.
\item \verb|hf| : Enable header and footer\footnote{You can enable
    the display of page numbers in the final version of the entire
    collection. In this case, you should adhere to the end-to-end
    pagination of individual papers.}.
\end{itemize}

\section{Front matter}

\subsection{Title Information}

The titles of papers should be either all use the emphasizing
capitalized style or they should all use the regular English (or
native language) style. It does not make a good impression if you or
your authors mix the styles.

Use the \verb|\title| command to define the title of your work. Do not
insert line breaks in your title.

\subsection{Title variants}

\verb|\title| command have the below options:
\begin{itemize}
\item \verb|title|: Document title. This is default option. 
\begin{lstlisting}
\title[mode=title]{This is a title}
\end{lstlisting}
You can just omit it, like as follows:
\begin{lstlisting}
\title{This is a title}
\end{lstlisting}

\item \verb|alt|: Alternate title.
\begin{lstlisting}
\title[mode=alt]{This is a alternate title}
\end{lstlisting}

\item \verb|sub|: Sub title.
\begin{lstlisting}
\title[mode=sub]{This is a sub title}
\end{lstlisting}
You can just use \verb|\subtitle| command, as follows:
\begin{lstlisting}
\subtitle{This is a sub title}
\end{lstlisting}

\item \verb|trans|: Translated title.
\begin{lstlisting}
\title[mode=trans]{This is a translated title}
\end{lstlisting}

\item \verb|transsub|: Translated sub title.
\begin{lstlisting}
\title[mode=transsub]{This is a translated sub title}
\end{lstlisting}
\end{itemize}

\subsection{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

\verb|\author| command have the below options:

\begin{itemize}
\item \verb|style| : Style of author name (chinese)
\item \verb|prefix| : Prefix
\item \verb|suffix| : Suffix
\item \verb|degree| : Degree
\item \verb|role| : Role
\item \verb|orcid| : ORCID
\item \verb|email| : E-mail
\item \verb|url| : URL
\end{itemize}

Author names can have some kinds of marks and notes:
\begin{itemize}
\item affiliation mark: \verb|\author[<num>]|.
\end{itemize}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}
\item Group the authors per affiliation.
\item Use an explicit mark to indicate the affiliations.
\end{enumerate}

Author block example:
\begin{lstlisting}
\author[1,2]{Author Name}[%
    prefix=Prof.,
    degree=D.Sc.,
    role=Researcher,
    orcid=0000-0000-000-0000,
    email=name@example.com,
    url=https://name.example.com
]

\address[1]{Affiliation #1}
\address[2]{Affiliation #2}
\end{lstlisting}

\subsection{Abstract and Keywords}

Abstract shall be entered in an environment that starts
with \verb|\begin{abstract}| and ends with
\verb|\end{abstract}|.

\begin{lstlisting}
\begin{abstract}
  This is an abstract.
\end{abstract}
\end{lstlisting}

The key words are enclosed in a \verb|keywords|
environment. Use \verb|\sep| to separate keywords.

\begin{lstlisting}
\begin{keywords}
  First keyword \sep 
  Second keyword \sep 
  Third keyword \sep 
  Fourth keyword
\end{keywords}
\end{lstlisting}

At the end of front matter add \verb|\maketitle| command.

\subsection{Various Marks in the Front Matter}

The front matter becomes complicated due to various kinds
of notes and marks to the title and author names. Marks in
the title will be denoted by a star ($\star$) mark;
footnotes are denoted by super scripted Arabic numerals,
corresponding author by an Conformal asterisk (*) mark.

\subsubsection{Title marks}

Title mark can be entered by the command, \verb|\tnotemark[<num>]|
and the corresponding text can be entered with the command
\verb|\tnotetext[<num>]{<text>}|. An example will be:

\begin{lstlisting}
\title{A better way to format your document for CEUR-WS}

\tnotemark[1]
\tnotetext[1]{You can use this document as the template for preparing your
  publication. We recommend using the latest version of the ceurart style.}
\end{lstlisting}

\verb|\tnotemark| and \verb|\tnotetext| can be anywhere in
the front matter, but should be before \verb|\maketitle| command.

\subsubsection{Author marks}

Author names can have some kinds of marks and notes:
\begin{itemize}
\item footnote mark : \verb|\fnmark[<num>]|
\item footnote text : \verb|\fntext[<num>]{<text>}|
\item corresponding author mark : \verb|\cormark[<num>]|
\item corresponding author text : \verb|\cortext[<num>]{<text>}|
\end{itemize}

\subsubsection{Other marks}

At times, authors want footnotes which leave no marks in
the author names. The note text shall be listed as part of
the front matter notes. Class files provides
\verb|\nonumnote| for this purpose. The usage
\begin{lstlisting}
\nonumnote{<text>}
\end{lstlisting}
and should be entered anywhere before the \verb|\maketitle|
command for this to take effect.

\section{Sectioning Commands}

Your work should use standard \LaTeX{} sectioning commands:
\verb|\section|, \verb|\subsection|,
\verb|\subsubsection|, and
\verb|\paragraph|. They should be numbered; do not remove
the numbering from the commands.

Simulating a sectioning command by setting the first word or words of
a paragraph in boldface or italicized text is not allowed.

\section{Tables}

The ``\verb|ceurart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

Table captions are placed \textit{above} the table.

Because tables cannot be split across pages, the best placement for
them is typically the top of the page nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \verb|table| to enclose the table's contents and the
table caption. The contents of the table itself must go in the
\verb|tabular| environment, to be aligned properly in rows and
columns, with the desired horizontal and vertical rules.

Immediately following this sentence is the point at which
Table~\ref{tab:freq} is included in the input file; compare the
placement of the table here with the table in the printed output of
this document.

\begin{table*}
  \caption{Frequency of Special Characters}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Non-English or Math&Frequency&Comments\\
    \midrule
    \O & 1 in 1,000& For Swedish names\\
    $\pi$ & 1 in 5& Common in math\\
    \$ & 4 in 5 & Used in business\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table*}

To set a wider table, which takes up the whole width of the page's
live area, use the environment \verb|table*| to enclose the table's
contents and the table caption.  As with a single-column table, this
wide table will ``float'' to a location deemed more
desirable. Immediately following this sentence is the point at which
Table~\ref{tab:commands} is included in the input file; again, it is
instructive to compare the placement of the table here with the table
in the printed output of this document.

\begin{table}
  \caption{Some Typical Commands}
  \label{tab:commands}
  \begin{tabular}{ccl}
    \toprule
    Command &A Number & Comments\\
    \midrule
    \texttt{{\char'134}author} & 100& Author \\
    \texttt{{\char'134}table}& 300 & For tables\\
    \texttt{{\char'134}table*}& 400& For wider tables\\
    \bottomrule
  \end{tabular}
\end{table}

\section{Math Equations}

You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of the three are
discussed in the next sections.

\subsection{Inline (In-text) Equations}

A formula that appears in the running text is called an inline or
in-text formula.  It is produced by the \verb|math| environment,
which can be invoked with the usual
\verb|\begin| \ldots \verb|\end| construction or with
the short form \verb|$| \ldots \verb|$|. You can use any of the symbols
and structures, from $\alpha$ to $\omega$, available in
\LaTeX~\cite{Lamport:LaTeX};
this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\begin{math}
  \lim_{n\rightarrow \infty} \frac{1}{n} = 0,
\end{math}
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsection{Display Equations}

A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \verb|equation|
environment. An unnumbered display equation is produced by the
\verb|displaymath| environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX{}; this section will just give a couple
of examples of display equations in context.  First, consider the
equation, shown as an inline equation above:
\begin{equation}
  \lim_{n\rightarrow \infty} \frac{1}{n} = 0.
\end{equation}
Notice how it is formatted somewhat differently in
the \verb|displaymath|
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}
  S_{n} = \sum_{i=1}^{n} x_{i} ,
\end{displaymath}
and follow it with another numbered equation:
\begin{equation}
  \lim_{x \to 0} (1 + x)^{1/x} = e
\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\section{Figures}

The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
\end{figure}

Your figures should contain a caption which describes the figure to
the reader. Figure captions go below the figure. Your figures should
also include a description suitable for screen readers, to
assist the visually-challenged to better understand your work.

Figure captions are placed below the figure.

\section{Citations and Bibliographies}

The use of Bib\TeX{} for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}|
command:
\begin{lstlisting}
\bibliography{bibfile}
\end{lstlisting}
where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
suffix, of the Bib\TeX{} file.

\subsection{Some examples}

A paginated journal article \cite{Abril07}, an enumerated journal
article \cite{Cohen07}, a reference to an entire issue
\cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
monograph/whole book in a series (see 2a in spec. document)
\cite{Harel79}, a divisible-book such as an anthology or compilation
\cite{Editor00} followed by the same example, however we only output
the series if the volume number is given \cite{Editor00a} (so series
should not be present since it has no vol. no.), a chapter in a
divisible book \cite{Spector90}, a chapter in a divisible book in a
series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97},
an article in a proceedings (of a conference, symposium, workshop for
example) (paginated proceedings article) \cite{Andler79}, a
proceedings article with all possible elements \cite{Smith10}, an
example of an enumerated proceedings article \cite{VanGundy07}, an
informally published work \cite{Harel78}, a doctoral dissertation
\cite{Clarkson85}, a master's thesis: \cite{anisi03}, an online
document / world wide web resource \cite{Thornburg01, Ablamowicz07,
  Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2)
\cite{Novak03} and \cite{Lee05} and (Case 3) a patent
\cite{JoeScientist001}, work accepted for publication \cite{rous08},
prolific author \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other
cites might contain `duplicate' DOI and URLs (some SIAM articles)
\cite{Kirschmer:2010:AEI:1958016.1958018}. Multi-volume works as books
\cite{MR781536} and \cite{MR781537}. A couple of citations with DOIs:
\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
citations: \cite{TUGInstmem, Thornburg01, R, UMassCitations}.

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{lstlisting}
\begin{acknowledgments}
  These are different acknowledgments.
\end{acknowledgments}
\end{lstlisting}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered
\verb|\section|; please use the ``\verb|acknowledgments|'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|\appendix|'' command:
\begin{lstlisting}
\appendix
\end{lstlisting}
and note that in the appendix, sections are lettered, not
numbered.

%%
%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to the developers of ACM consolidated LaTeX styles
  \url{https://github.com/borisveytsman/acmart} and to the developers
  of Elsevier updated \LaTeX{} templates
  \url{https://www.ctan.org/tex-archive/macros/latex/contrib/els-cas-templates}.  
\end{acknowledgments}

%%
%% Define the bibliography file to be used
\bibliography{sample-ceur}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Online Resources}

The sources for the ceur-art style are available via
\begin{itemize}
\item \href{https://github.com/yamadharma/ceurart}{GitHub},
% \item \href{https://www.overleaf.com/project/5e76702c4acae70001d3bc87}{Overleaf},
\item
  \href{https://www.overleaf.com/latex/templates/template-for-submissions-to-ceur-workshop-proceedings-ceur-ws-dot-org/pkfscdkgkhcq}{Overleaf
    template}.
\end{itemize}

\end{document}

%%
%% End of file

### 2024-04-22 paper/paper-part2.tex
refactor literature search for #3

@@
 Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.
+
+Examples further include ``production ready systems'' like NBoost for ElasticSearch.\footnote{\url{https://github.com/koursaros-ai/nboost}}
+
+- NBoost is a scalable, search-api-boosting platform for deploying
+transformer models to improve the relevance of search results or
+diffe rent platforms (i.e. Elasticsearch) Topics
+- maybe more useful for the user pipeline
+- is between user and the actual pipeline where it picks the best
+based on relevance and training
+
+JMC and DISP~\cite{cui21}:
+- Joint Model Compression (JMC)
+- Direct Importance-aware Structured Pruning
+- Dense Knowledge Distillation (DKD)
+- Paper at thulb
+
+MiniLMv2~\cite{wang21} (https://huggingface.co/sentence-transformers/all-MiniLM-L6-v2)
+- found in https://arxiv.org/abs/2012.15828 (MiniLMv2)
+- they state that their model outperform state of the art models
+- uses deep distillated self-attention which are distributed and also
+give values to relations to copy teacher self-attention
+- transfers knowledge of upper-middle- to last-layer(MiniLM only
+mimics the last layer)
+
+Transit(https://arxiv.org/abs/2101.03289)

### 2024-04-22 code/cross-encoder.py
feat: preparing data for training #2

@@ -1,0 +1,67 @@
+import pandas as pd
+from datasets import Dataset, DatasetDict
+from transformers import AutoTokenizer, DataCollatorWithPadding
+from transformers import TrainingArguments, Trainer
+from transformers import AutoModel, AutoModelForSequenceClassification
+from evaluate import load
+import numpy as np
+from torch.utils.data import DataLoader
+from sentence_transformers import CrossEncoder, SentenceTransformer
+import torch
+import sentence_transformers
+
+# For a full training on the msmarco dataset we decided to use the
+# msmarco-passage_train_triples-small dataset.
+# This is already provided by the huggingface datasets library.
+# https://huggingface.co/datasets/irds/msmarco-passage_train_triples-small
+
+
+# https://huggingface.co/docs/datasets/tabular_load#pandas-dataframes
+# load Dataset from Pandas DataFrame
+raw_input = pd.read_json("../data/triples-ms-marco-tiny.jsonl.gz", encoding="utf-8", lines=True)
+df = []
+
+for _, i in df.iterrows():
+    df += [
+        {'query': i["query"],
+         'text': i["postive_document"],
+         'label': 1},
+        {'query': i["query"],
+         'text': i["negative_passage"],
+         'label': 0}
+    ]
+
+training_data = Dataset.from_pandas(pd.DataFrame(df))
+
+
+# The model we want to fine-tune
+checkpoint = "bert-base-uncased"
+train_batch_size = 32
+num_epochs = 1
+
+# We set num_labels=1 and set the activation function to Identity, so that we get the raw logits
+model = CrossEncoder(checkpoint, num_labels=1, max_length=512)
+
+# We create a DataLoader to load our train samples
+# train_dataloader = DataLoader(raw_datasets, shuffle=True, batch_size=train_batch_size)
+
+# We define our loss funtion
+loss_function = torch.nn.BCEWithLogitsLoss()
+
+# TODO: write training with (fit) method
+# TODO: write training loop
+
+'''
+# Train the model
+model.fit(
+    train_dataloader=train_dataloader,
+    evaluator=evaluator,
+    epochs=num_epochs,
+    evaluation_steps=10000,
+    warmup_steps=warmup_steps,
+    use_amp=True,
+)
+'''
+
+# Save latest model
+model.save("cross-encoder-ms-marco-tiny")

### 2024-04-22 paper/paper.tex
refactor literature search for #3

@@
 and structures, from $\alpha$ to $\omega$, available in
-\LaTeX~\cite{Lamport:LaTeX};
+\LaTeX
 this section will simply show a few
@@
 
-\subsection{Some examples}
-
-A paginated journal article \cite{Abril07}, an enumerated journal
-article \cite{Cohen07}, a reference to an entire issue
-\cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
-monograph/whole book in a series (see 2a in spec. document)
-\cite{Harel79}, a divisible-book such as an anthology or compilation
-\cite{Editor00} followed by the same example, however we only output
-the series if the volume number is given \cite{Editor00a} (so series
-should not be present since it has no vol. no.), a chapter in a
-divisible book \cite{Spector90}, a chapter in a divisible book in a
-series \cite{Douglass98}, a multi-volume work as book \cite{Knuth97},
-an article in a proceedings (of a conference, symposium, workshop for
-example) (paginated proceedings article) \cite{Andler79}, a
-proceedings article with all possible elements \cite{Smith10}, an
-example of an enumerated proceedings article \cite{VanGundy07}, an
-informally published work \cite{Harel78}, a doctoral dissertation
-\cite{Clarkson85}, a master's thesis: \cite{anisi03}, an online
-document / world wide web resource \cite{Thornburg01, Ablamowicz07,
-  Poker06}, a video game (Case 1) \cite{Obama08} and (Case 2)
-\cite{Novak03} and \cite{Lee05} and (Case 3) a patent
-\cite{JoeScientist001}, work accepted for publication \cite{rous08},
-prolific author \cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other
-cites might contain `duplicate' DOI and URLs (some SIAM articles)
-\cite{Kirschmer:2010:AEI:1958016.1958018}. Multi-volume works as books
-\cite{MR781536} and \cite{MR781537}. A couple of citations with DOIs:
-\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
-citations: \cite{TUGInstmem, Thornburg01, R, UMassCitations}.
-
 \section{Acknowledgments}

### 2024-04-22 code/cross-encoder.py
feat: first attempt of fit training cross-encoder #2)

@@ -8,6 +8,7 @@ import numpy as np
 from torch.utils.data import DataLoader
 from sentence_transformers import CrossEncoder, SentenceTransformer
 import torch
+from sentence_transformers import InputExample
 import sentence_transformers
 
 # For a full training on the msmarco dataset we decided to use the
@@ -21,18 +22,18 @@ import sentence_transformers
 raw_input = pd.read_json("../data/triples-ms-marco-tiny.jsonl.gz", encoding="utf-8", lines=True)
 df = []
 
-for _, i in df.iterrows():
+for _, i in raw_input.iterrows():
     df += [
-        {'query': i["query"],
-         'text': i["postive_document"],
-         'label': 1},
-        {'query': i["query"],
-         'text': i["negative_passage"],
-         'label': 0}
+        InputExample(texts=[i["query"], i["positive_document"]], label=1),
+    ]
+    df += [
+        InputExample(texts=[i["query"], i["negative_passage"]], label=0),
     ]
 
-training_data = Dataset.from_pandas(pd.DataFrame(df))
+# training_data = Dataset.from_pandas(pd.DataFrame(df))
 
+# print(training_data)
+# print(training_data[0])
 
 # The model we want to fine-tune
 checkpoint = "bert-base-uncased"
@@ -43,7 +44,10 @@ num_epochs = 1
 model = CrossEncoder(checkpoint, num_labels=1, max_length=512)
 
 # We create a DataLoader to load our train samples
-# train_dataloader = DataLoader(raw_datasets, shuffle=True, batch_size=train_batch_size)
+train_dataloader = DataLoader(df, shuffle=True, batch_size=train_batch_size)
+
+# Print the first entry in train_dataloader
+# print(next(iter(train_dataloader)))
 
 # We define our loss funtion
 loss_function = torch.nn.BCEWithLogitsLoss()
@@ -52,16 +56,39 @@ loss_function = torch.nn.BCEWithLogitsLoss()
 # TODO: write training loop
 
 '''
+for epoch in range(num_epochs):
+    model.model.train()
+    for i, batch in enumerate(train_dataloader):
+        # print(i, batch)
+        queries = batch["query"]
+        passages = batch["text"]
+        labels = batch["labels"]
+
+        # Forward pass
+        scores = model.predict([queries, passages], show_progress_bar=True)
+
+        # Compute loss
+        loss = loss_function(scores, labels)
+
[…]

### 2024-05-23 paper/cross-encoder.tex
doc: how we choosed hyperparameters and results #7

To determine the appropriate hyperparameters for our training system, we systematically evaluated various parameters and the performance of the resulting cross-encoder models. This method ensures that the model achieves a high Mean Reciprocal Rank (recip\_rank) and a high Normalized Discounted Cumulative Gain (ndcg\_cut.10). Our evaluation focused on four primary parameters: batch size, learning rate, and the effect of randomly initialized weight matrices.

Initially, hyperparameters were intuitively selected and designated as the baseline model, reflecting the default values of the training method employed. To explore alternative hyperparameters, we tested values both below and above the defaults. For each parameter to be fine-tuned, three different values were selected. Each parameter was altered individually with respect to the baseline, resulting in the generation, training, and evaluation of 13 models in total. This approach ensures a comprehensive assessment of each hyperparameter's impact on model performance.

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
index & name & bs & epochs & lr & seed & ndcg\_cut.10 & recip\_rank \\
\hline
0 & BM25 & & & & & 0.4795 & 0.7950 \\
\hline
\multicolumn{8}{|c|}{base line:} \\
\hline
1 & cross-encoder- & 32 & 10 & 2e-5 & 233 & 0.6251 & 0.9162 \\
\hline
\multicolumn{8}{|c|}{batch size:} \\
\hline
2 & cross-encoder- & 16 & 10 & 2e-5 & 233 & 0.6045 & 0.8901 \\
3 & cross-encoder- & 64 & 10 & 2e-5 & 233 & 0.6309 & 0.9147 \\
4 & cross-encoder- & 128 & 10 & 2e-5 & 233 & 0.6248 & 0.8904 \\
\hline
\multicolumn{8}{|c|}{epochs:} \\
\hline
5 & cross-encoder- & 32 & 5 & 2e-5 & 233 & 0.6100 & 0.9036 \\
6 & cross-encoder- & 32 & 15 & 2e-5 & 233 & 0.6380 & 0.9005 \\
7 & cross-encoder- & 32 & 20 & 2e-5 & 233 & 0.6319 & 0.9009 \\
\hline
\multicolumn{8}{|c|}{learning rate} \\
\hline
8 & cross-encoder- & 32 & 10 & 1e-5 & 233 & 0.6040 & 0.9152 \\
9 & cross-encoder- & 32 & 10 & 1e-4 & 233 & 0.5832 & 0.8843 \\
10 & cross-encoder- & 32 & 10 & 5e-4 & 233 & 0.5129 & 0.8502 \\
\hline
\multicolumn{8}{|c|}{seed:} \\
\hline
11 & cross-encoder- & 32 & 10 & 2e-5 & 5 & 0.6241 & 0.9044 \\
12 & cross-encoder- & 32 & 10 & 2e-5 & 6765 & 0.6170 & 0.9068 \\
13 & cross-encoder- & 32 & 10 & 2e-5 & 46368 & 0.6200 & 0.8947 \\
\hline
\end{tabular}
\caption{Evaluation of Cross-Encoder Models with Various Hyperparameters}
\label{table:cross_encoder}
\end{table}

### 2024-05-23 code/cross-encoder-benchmark.py

@@ -83,21 +83,21 @@ for batch_size in train_batch_sizes:
           baseline_num_epochs,
           baseline_learning_rate,
           baseline_random_seed,
-          f"cross-encoder-{batch_size}-10-2e5-42")
+          f"cross-encoder-{batch_size}-10-2e5-233")
 
 for num_epochs in train_num_epochs:
     train(baseline_batch_size,
           num_epochs,
           baseline_learning_rate,
           baseline_random_seed,
-          f"cross-encoder-32-{num_epochs}-2e5-42")
+          f"cross-encoder-32-{num_epochs}-2e5-233")
 
 for learning_rate in train_learning_rates:
     train(baseline_batch_size,
           baseline_num_epochs,
           learning_rate,
           baseline_random_seed,
-          f"cross-encoder-32-10-{learning_rate}-42")
+          f"cross-encoder-32-10-{learning_rate}-233")
 
 for random_seed in train_random_seeds:
     train(baseline_batch_size,

### 2024-05-27 paper/paper-part2.tex
why did we choose TinyBert

@@
 
-From~\cite{jiao20}: Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks.
-However, pre-trained language models are usually computationally expensive, so it is difficult to efficiently execute them on resource-restricted devices.
-To accelerate inference and reduce model size while maintaining accuracy, we first propose a novel Transformer distillation method that is specially designed for knowledge distillation (KD) of the Transformer-based models.
-By leveraging this new KD method, the plenty of knowledge encoded in a large teacher BERT can be effectively transferred to a small student Tiny-BERT.
-Then, we introduce a new two-stage learning framework for TinyBERT, which performs Transformer distillation at both the pretraining and task-specific learning stages.
-This framework ensures that TinyBERT can capture he general-domain as well as the task-specific knowledge in BERT.
-TinyBERT with 4 layers is empirically effective and achieves more than 96.8\% the performance of its teacher BERTBASE on GLUE benchmark, while being 7.5x smaller and 9.4x faster on inference.
-TinyBERT with 4 layers is also significantly better than 4-layer state-of-the-art baselines on BERT distillation, with only about 28\% parameters and about 31\% inference time of them.
-Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.
+From~\cite{jiao20}: TinyBERT offers several advantages over other models, especially when it comes to efficiency and performance.
+One of the primary benefits is its reduced size and faster inference time.
+TinyBERT4, which comprises only four layers, is 7.5 times smaller and 9.4 times faster than its teacher model, BERTBASE.
+Despite this significant reduction in size, TinyBERT4 achieves more than 96.8\% of the performance of BERTBASE on the GLUE benchmark tasks, demonstrating that it can maintain high accuracy while being substantially more efficient.
+This makes TinyBERT particularly suitable for applications on resource-restricted devices where computational power and memory are limited.
+
+Furthermore, TinyBERT employs a novel two-stage learning framework that involves both general distillation and task-specific distillation.
+In the general distillation stage, TinyBERT learns from the original BERT model without fine-tuning, capturing general domain knowledge.
+Subsequently, task-specific distillation is performed using fine-tuned BERT, allowing TinyBERT to absorb knowledge tailored to specific tasks.
+This two-stage process ensures that TinyBERT not only inherits the rich, general knowledge from BERT but also hones its performance on specific tasks, thereby improving its adaptability and effectiveness in various natural language processing tasks.
+
+Moreover, TinyBERT's distillation process includes advanced techniques such as attention-based and hidden states-based distillation.
+These techniques are designed to transfer the linguistic knowledge encoded in the teacher model's attention weights and hidden states to the student model.
+This method helps TinyBERT retain essential linguistic features, which are crucial for tasks involving syntax and coreference resolution.
+The complementary nature of these distillation methods ensures that TinyBERT can achieve high performance even with fewer parameters and reduced computational requirements.
+
+Finally, TinyBERT demonstrates superior performance compared to other state-of-the-art models designed for model compression.
+For instance, TinyBERT4 significantly outperforms other 4-layer models like BERT4-PKD and DistilBERT4 by at least 4.4\%, while using only about 28\% of the parameters and 31\% of the inference time of these models .
+When scaled up to six layers, TinyBERT6 achieves performance on par with BERTBASE, making it a robust and scalable solution for diverse NLP tasks.
+These benefits collectively highlight why TinyBERT is an excellent choice for applications requiring efficient and high-performing language models.\\
 

### 2024-06-03 data/bm25_scoring.py
prepare bm25 scoring

@@ -1,0 +1,13 @@
+import pyterrier as pt
+from os.path import abspath
+
+if not pt.started():
+    pt.init()
+    index = pt.IndexRef.of(abspath('index'))
+    index = pt.IndexFactory.of(index)
+
+def bm25_score(qid, docnos):
+    global index
+
+    return None
+

### 2024-06-03 data/extract_data.py

@@ -1,6 +1,7 @@
 #!/usr/bin/env python3
 from tqdm import tqdm
 import pandas as pd
+from bm25_scoring import bm25_score
 
 
 def parse_tsv(file_name):

### 2024-06-03 data/extract_rank_distill_llm.py

@@ -5,6 +5,7 @@ import ir_datasets
 import gzip
 from tqdm import tqdm
 import json
+from bm25_scoring import bm25_score
 
 dataset = ir_datasets.load("msmarco-passage/train")
 

### 2024-06-03 data/bm25_scoring.py
mf

@@ -1,13 +1,26 @@
 import pyterrier as pt
 from os.path import abspath
+import pandas as pd
 
 if not pt.started():
     pt.init()
     index = pt.IndexRef.of(abspath('index'))
     index = pt.IndexFactory.of(index)
+    tokeniser = pt.autoclass("org.terrier.indexing.tokenisation.Tokeniser").getTokeniser()
 
-def bm25_score(qid, docnos):
+def pt_tokenise(text):
+    return ' '.join(tokeniser.getTokens(text))
+
+def bm25_score(query, docnos):
     global index
+    pipeline = pt.FeaturesBatchRetrieve(index, wmodel="TF", features=["WMODEL:BM25", "WMODEL:TF", "WMODEL:TF-IDF", "WMODEL:PL2", "WMODEL:DirichletLM"])
+
+    df = []
+    for docno in docnos:
+        df += [{
+            'qid': '1', 'query': pt_tokenise(query),
+            'docno': docno,
+        }]
 
     return None
 

### 2024-06-03 data/bm25_scoring.py
mf

@@ -24,3 +24,7 @@ def bm25_score(query, docnos):
 
     return None
 
+if __name__ == '__main__':
+    #export IR_DATASETS_HOME="/mnt/ceph/storage/data-tmp/current/kibi9872/.ir_datasets"
+    bm25_score('hello world', ['7694473', '4373328'])
+

### 2024-06-03 data/bm25_scoring.py
add bm25 scores for distillation data

@@ -13,18 +13,21 @@ def pt_tokenise(text):
 
 def bm25_score(query, docnos):
     global index
-    pipeline = pt.FeaturesBatchRetrieve(index, wmodel="TF", features=["WMODEL:BM25", "WMODEL:TF", "WMODEL:TF-IDF", "WMODEL:PL2", "WMODEL:DirichletLM"])
+    pipeline = pt.FeaturesBatchRetrieve(index, wmodel="None", features=["WMODEL:BM25", "WMODEL:TF_IDF", "WMODEL:DirichletLM", "WMODEL:PL2"])
+    pipeline.wmodel = None
 
     df = []
     for docno in docnos:
-        df += [{
-            'qid': '1', 'query': pt_tokenise(query),
-            'docno': docno,
-        }]
+        df += [{'qid': '1', 'query': pt_tokenise(query), 'docno': docno, 'score': 10000 - len(df)}]
+    df = pd.DataFrame(df)
 
-    return None
+    ret = {}
+    for _, i in pipeline(df).iterrows():
+        ret[i['docno']] = {'BM25': i['features'][0], 'TF_IDF': i['features'][1], 'DirichletLM': i['features'][2], 'PL2': i['features'][3]}
+
+    return ret
 
 if __name__ == '__main__':
     #export IR_DATASETS_HOME="/mnt/ceph/storage/data-tmp/current/kibi9872/.ir_datasets"
-    bm25_score('hello world', ['7694473', '4373328'])
+    print(bm25_score('hello world', ['7694473', '4373328']))
 

### 2024-06-03 data/extract_rank_distill_llm.py

@@ -22,7 +22,22 @@ def queries():
 if __name__ == '__main__':
     q = queries()
     docs_store = dataset.docs_store()
-    with gzip.open('rank-distill-llm.jsonl.gz', 'wt') as f:
-        for i in tqdm(list(scored_docs().scoreddocs_iter())):
-            f.write(json.dumps({'query_id': i.query_id, 'doc_id': i.doc_id, 'score': i.score, 'query': q[i.query_id], 'text': docs_store.get(i.doc_id).default_text()}) + '\n')
+    ret = []
+    qid_to_docs = {}
+    qid_to_doc_scores = {}
 
+    for i in list(scored_docs().scoreddocs_iter()):
+        if i.query_id not in qid_to_docs:
+            qid_to_docs[i.query_id] = set()
+        qid_to_docs[i.query_id].add(i.doc_id)
+
+    for qid, docids in tqdm(qid_to_docs.items(), 'Score Queries'):
+        qid_to_doc_scores[qid] = bm25_score(q[qid], docids)
+
+    for i in tqdm(list(scored_docs().scoreddocs_iter()), 'Get Document Texts'):
+        ret += [{'query_id': i.query_id, 'doc_id': i.doc_id, 'score': i.score, 'query': q[i.query_id], 'text': docs_store.get(i.doc_id).default_text(), 'scores': qid_to_doc_scores[qid][i.doc_id]}]
+
+
+    with gzip.open('rank-distill-llm.jsonl.gz', 'wt') as f:
+        for i in ret:
+            f.write(json.dumps(i))

### 2024-06-03 data/extract_data.py
mf

@@ -2,23 +2,37 @@
 from tqdm import tqdm
 import pandas as pd
 from bm25_scoring import bm25_score
+from extract_rank_distill_llm import queries
+import json
 
+def build_doc_to_docno(file_name):
+    ret = {}
+    with open(file_name, 'r') as f:
+        for i in tqdm(f, 'Document Index'):
+            i = json.loads(i)
+            ret[i['text'].lower().strip()] = i['docno']
 
-def parse_tsv(file_name):
+    return ret
+
+def parse_tsv(file_name, doc_to_docno):
     with open(file_name, 'r') as f:
         covered_queries = set()
-        for doc in tqdm(f):
+        for doc in tqdm(f, 'triples'):
             query, positive_passage, negative_passage = doc.split('\t')
             if query in covered_queries:
                 continue
-
+            positive_id = doc_to_docno.get(positive_passage.lower().strip())
+            negative_id = doc_to_docno.get(negative_passage.lower().strip())
+            if positive_id is None or negative_id is None:
+                continue
             covered_queries.add(query)
-            yield {'query': query, 'positive_document': positive_passage, 'negative_passage': negative_passage}
+            yield {'query': query, 'positive_document': positive_passage, 'negative_passage': negative_passage, 'id_positive_document': positive_id, 'id_negative_document': negative_id}
 
         print(f'Processed {len(covered_queries)} queries')
 
 
 if __name__ == '__main__':
-    df = list(parse_tsv('triples.train.small.tsv'))
+    doc_to_docno = build_doc_to_docno('documents.jsonl')
+    df = list(parse_tsv('triples.train.small.tsv', doc_to_docno))
     print(len(df))
     pd.DataFrame(df).to_json('triples-train.jsonl.gz', lines=True, orient='records')

### 2024-06-03 data/extract_rank_distill_llm.py

@@ -35,9 +35,8 @@ if __name__ == '__main__':
         qid_to_doc_scores[qid] = bm25_score(q[qid], docids)
 
     for i in tqdm(list(scored_docs().scoreddocs_iter()), 'Get Document Texts'):
-        ret += [{'query_id': i.query_id, 'doc_id': i.doc_id, 'score': i.score, 'query': q[i.query_id], 'text': docs_store.get(i.doc_id).default_text(), 'scores': qid_to_doc_scores[qid][i.doc_id]}]
-
+        ret += [{'query_id': i.query_id, 'doc_id': i.doc_id, 'score': i.score, 'query': q[i.query_id], 'text': docs_store.get(i.doc_id).default_text(), 'scores': qid_to_doc_scores[i.query_id][i.doc_id]}]
 
     with gzip.open('rank-distill-llm.jsonl.gz', 'wt') as f:
         for i in ret:
-            f.write(json.dumps(i))
+            f.write(json.dumps(i) + '\n')

### 2024-06-03 code/bm25-fine-tuning.py
feat: added bm25 fine tuning for tiny trainig data set #6

@@ -1,0 +1,109 @@
+"""
+This examples show how to train a Cross-Encoder for the MS Marco dataset
+(https://github.com/microsoft/MSMARCO-Passage-Ranking).
+
+In this example we use a knowledge distillation setup. Sebastian Hofstätter et al. trained in
+https://arxiv.org/abs/2010.02666 an ensemble of large Transformer models for the MS MARCO datasets
+and combines the scores from a BERT-base, BERT-large, and ALBERT-large model.
+
+We use the logits scores from the ensemble to train a smaller model. We found that the MiniLM model gives the best
+performance while offering the highest speed.
+
+The resulting Cross-Encoder can then be used for passage re-ranking: You retrieve for example 100 passages
+for a given query, for example with ElasticSearch, and pass the query+retrieved_passage to the CrossEncoder
+for scoring. You sort the results then according to the output of the CrossEncoder.
+
+This gives a significant boost compared to out-of-the-box ElasticSearch / BM25 ranking.
+
+Running this script:
+python train_cross-encoder-v2.py
+"""
+from torch.utils.data import DataLoader
+from sentence_transformers import LoggingHandler, util
+from sentence_transformers.cross_encoder import CrossEncoder
+
+from sentence_transformers import InputExample
+import logging
+from datetime import datetime
+import gzip
+import os
+import tarfile
+import tqdm
+import torch
+import json
+import pandas as pd
+
+logging.basicConfig(format='%(asctime)s - %(message)s',
+                    datefmt='%Y-%m-%d %H:%M:%S',
+                    level=logging.INFO,
+                    handlers=[LoggingHandler()])
+# /print debug information to stdout
+
+# We make a directory for storing the MS Marco dataset
+data_path = '../data/triples-ms-marco-tiny-with-bm25.jsonl.gz'
+
+raw_input = pd.read_json(data_path, encoding="utf-8", lines=True)
+
+# Read the corpus files, that contain all the passages. Store them in the corpus dict
+corpus = {}
+
+# Read the train queries, store in queries dict
+queries = {}
+
+# Loading injection scores and applying normalization (global min-max in the paper)
+global_min_bm25 = 0
+global_max_bm25 = 50
+scores = {}
+
+train_samples = []
+
+for _, i in raw_input.iterrows():
+    corpus[i["id_positive_document"]] = i["positive_document"]
+    corpus[i["id_negative_document"]] = i["negative_passage"]
+
[…]

### 2024-06-03 code/cross-encoder.py

@@ -37,7 +37,7 @@ for _, i in raw_input.iterrows():
 
 # The model we want to fine-tune
 checkpoint = "prajjwal1/bert-tiny"
-train_batch_size = 200
+train_batch_size = 32
 num_epochs = 10
 
 # We set num_labels=1 and set the activation function to Identity, so that we get the raw logits

### 2024-06-03 data/extract_data_1gb.py

@@ -1,0 +1,28 @@
+#!/usr/bin/env python3
+from tqdm import tqdm
+import pandas as pd
+
+
+def parse_tsv(file_name):
+    with open(file_name, 'r') as f:
+        covered_queries = set()
+        queries = {}
+        for doc in tqdm(f):
+            query, positive_passage, negative_passage = doc.split('\t')
+            if query in covered_queries and queries[query] < 10:
+                queries[query] += 1
+            elif query not in covered_queries:
+                queries[query] = 1
+            else:
+                continue
+
+            covered_queries.add(query)
+            yield {'query': query, 'positive_document': positive_passage, 'negative_passage': negative_passage}
+
+        print(f'Processed {len(covered_queries)} queries')
+
+
+if __name__ == '__main__':
+    df = list(parse_tsv('triples.train.small.tsv'))
+    print(len(df))
+    pd.DataFrame(df).to_json('test.jsonl.gz', lines=True, orient='records')

### 2024-06-24 data/extract_msmarco_dev.py
prepare ms-marco dev dataset for our model selection. #11

@@ -1,0 +1,18 @@
+#!/usr/bin/env python3
+#export IR_DATASETS_HOME=/mnt/ceph/tira/state/ir_datasets/
+import ir_datasets
+from trectools import TrecRun
+from tqdm import tqdm
+import gzip
+import json
+
+queries = {i.query_id: i.default_text() for i in ir_datasets.load("msmarco-passage/dev/small").queries_iter()}
+docsstore = ir_datasets.load("msmarco-passage").docs_store()
+
+run = TrecRun('/mnt/ceph/storage/web/files/data-in-progress/data-research/web-search/reneuir-24/msmarco-dev-dataset/msmarco-passage-dev-small.run').run_data
+run = run[run['rank'] <= 100]
+
+with gzip.open('rerank.jsonl.gz', 'wt') as f:
+    for _, i in tqdm(run.iterrows(), total=len(run)):
+        f.write(json.dumps({"qid": str(i['query']), "query": queries[str(i['query'])], "original_query": {}, "docno": i['docid'], "text": docsstore.get(i['docid']).default_text(), "original_document": {}, "rank": i['rank'], "score": i['score']}) + '\n')
+

### 2024-06-24 code/lightning-ir/rerank-with-model.sh
prepare usage of lightning ir

@@ -2,7 +2,7 @@
 
 lightning-ir re_rank \
 	--config config/tinybert-inference.yaml \
-	--data.inference_datasets.init_args.run_path msmarco-passage-trec-dl-2019-judged-20230107-training-rerank.jsonl.gz \
-	--trainer.callbacks.init_args.save_dir runs/${1}/ \
-	--model.init_args.model_name_or_path lightning_logs/${1}/huggingface_checkpoint/
+	--data.inference_datasets.init_args.run_path ${1}/rerank.jsonl.gz \
+	--trainer.callbacks.init_args.save_dir ${2}/ \
+	--model.init_args.model_name_or_path ${MODEL}
 

### 2024-06-24 code/lightning-ir/rerank-with-model.sh
Add evaluation for lightning ir for ticket #11

@@ -1,8 +1,10 @@
 #!/usr/bin/bash
 
 lightning-ir re_rank \
-	--config config/tinybert-inference.yaml \
-	--data.inference_datasets.init_args.run_path ${1}/rerank.jsonl.gz \
-	--trainer.callbacks.init_args.save_dir ${2}/ \
+	--config ${CONFIG_DIR}/tinybert-inference.yaml \
+	--data.inference_datasets.init_args.run_path ${inputDataset}/rerank.jsonl.gz \
+	--trainer.callbacks.init_args.save_dir ${outputDir}/ \
 	--model.init_args.model_name_or_path ${MODEL}
+
+mv ${outputDir}/rerank.run ${outputDir}/run.txt
 

### 2024-06-24 code/lightning-ir/run-all-models-on-validation-dataset.sh

@@ -1,0 +1,15 @@
+#!/usr/bin/bash
+
+for MODEL in $(find -L -iname huggingface_checkpoint|awk -F '/' '{print $3}'|sort -u)
+do
+	echo "Run predictions with ${MODEL}"
+	docker run --rm -ti \
+	    --network=none \
+	    -v ${PWD}/msmarco-dev/:/input-data:ro \
+	    -v ${PWD}/output-runs/${MODEL}:/runs \
+	    -v ${PWD}/lightning_logs/${MODEL}/huggingface_checkpoint/:/model \
+	    -e MODEL=/model \
+	    -e inputDataset=/input-data \
+	    -e outputDir=/runs \
+	    tiny-lightning-ir
+done

### 2024-06-24 paper/paper-part2.tex
Introductin added

--- 2024-04-22 paper/paper-part2.tex
@@
 
-From~\cite{jiao20}: Language model pre-training, such as BERT, has significantly improved the performances of many natural language processing tasks.
-However, pre-trained language models are usually computationally expensive, so it is difficult to efficiently execute them on resource-restricted devices.
-To accelerate inference and reduce model size while maintaining accuracy, we first propose a novel Transformer distillation method that is specially designed for knowledge distillation (KD) of the Transformer-based models.
-By leveraging this new KD method, the plenty of knowledge encoded in a large teacher BERT can be effectively transferred to a small student Tiny-BERT.
-Then, we introduce a new two-stage learning framework for TinyBERT, which performs Transformer distillation at both the pretraining and task-specific learning stages.
-This framework ensures that TinyBERT can capture he general-domain as well as the task-specific knowledge in BERT.
-TinyBERT with 4 layers is empirically effective and achieves more than 96.8\% the performance of its teacher BERTBASE on GLUE benchmark, while being 7.5x smaller and 9.4x faster on inference.
-TinyBERT with 4 layers is also significantly better than 4-layer state-of-the-art baselines on BERT distillation, with only about 28\% parameters and about 31\% inference time of them.
-Moreover, TinyBERT with 6 layers performs on-par with its teacher BERTBASE.
+From~\cite{jiao20}: There are many advantages to TinyBERT compared to others, especially in efficiency and performance.
+Among them, one significant benefit is the reduced size with faster inference time: TinyBERT4, which contains only four layers, is 7.5 times smaller with 9.4 times faster than its teacher model, BERTBASE.
+Even with this massive drop in model size, TinyBERT4 can achieve more than 96.8\% of the performance compared to BERTBASE on all GLUE benchmark tasks, which proves that it can hold a high degree of accuracy while being substantially more efficient.
+In that case, TinyBERT will be particularly fitting for applications executed on devices under highly resource-restrictive conditions with limited computational power and memory.
+
+Another major innovation of TinyBERT, however, is a new two-stage learning framework that includes general and task-specific distillation.
+The first is the general distillation stage, in which TinyBERT learns from the original BERT for general domain knowledge mastery.
+After that, it will conduct task-specific distillation with the fine-tuned BERT for some downstream tasks so that task-specific knowledge can be absorbed into TinyBERT.
+In this two-phase process, the TinyBERT inherits all the rich, general knowledge from BERT and can further enhance its performance on specific tasks, making it more adaptable and effective in various natural language processing tasks.
+
+More than that, TinyBERT's advanced distillation techniques include attention-based and hidden states-based ones.
+Specifically, these methods have been designed to distill the linguistic knowledge the teacher model has encoded in its attention weights and hidden states into the student model.
+When distilling, this technique enables TinyBERT to retain all essential features concerning syntax and coreference resolution tasks.
+The complementarity of these distillation techniques makes it possible for TinyBERT, with fewer parameters and reduced computational cost, to realize high performance.
+Finally, TinyBERT shows better performance compared with the other state-of-the-art models mainly designed for model compression.
+As shown, TinyBERT4 significantly outperforms other 4-layer models like BERT4-PKD and DistilBERT4 by at least 4.4\% while having only about 28\% of parameters and 31\% of inference time compared to these models.
+When scaled up to six layers, TinyBERT6 is on par with BERTBASE in performance; therefore, this makes it a relatively robust and scalable solution for a wide array of NLP tasks.
+Of course, all these advantages make TinyBERT one of the best choices for an application requiring efficient, high-performance language models.\\
 

### 2024-06-24 paper/paper.tex
Introductin added

@@
 
-CEUR-WS's article template provides a consistent \LaTeX{} style for
-use across CEUR-WS publications, and incorporates accessibility and
-metadata-extraction functionality. This document will explain the
-major features of the document class.
+Neural Information Retrieval has been a sea change for the field of Information Retrieval, driving unparalleled effectiveness improvements across a broad portfolio of IR tasks.
+However, these complex neural models bring traditional challenges in terms of much-needed computational resources, especially for efficient training and inference.
+This efficacy vs.
+computational cost dichotomy enforces the need for global evaluation of NIR methods by performance and resources.
+The third ReNeuIR Workshop, co-located with ACM SIGIR, will occur in Washington D.C., USA, in July 2024.
+It thus furthers a critical discourse on the efficiency of NIR models, including empirical justifications for increasing model complexity into daylight, urging resource-efficient model developments, and total evaluation frameworks accounting for quality, efficiency, and environmental impacts.
 
-If you are new to publishing with CEUR-WS, this document is a valuable
-guide to the process of preparing your work for publication.
+Our contribution to this discourse is also focused on optimizing TinyBERT, a lightweight language model.
+First, we will train various models with gradually tuned hyperparameters toward their minimization in size, subject to effectiveness.
+Such techniques shall be utilized at the interaction between hyperparameter optimization and model pruning for these goals.
+
+To further boost the performance of our optimized TinyBERT models, we incorporate BM25 scores.
+Since BM25 has been one of the most successful traditional IR models based on probabilistic retrieval, we would like to combine the BM25 scores and the output from TinyBERT to create a synergistic effect for better retrieval performance without adding too much computational overhead.
+
+Moreover, knowledge distillation will be utilized to gain efficiency and effectiveness.
+That is transferring knowledge from a large, well-performing teacher model to a smaller, more efficient student model.
+We can expect iterative distillation and finetuning to realize models that balance high effectiveness with low computational requirements.
+
+This paper discusses an in-depth understanding of TinyBERT with hyperparameter optimization, BM25 integration, and knowledge distillation toward developing efficient NIR models.
+We work towards a long-term vision for sustainable and effective neural information retrieval—themes and motivations that best fit the ReNeuIR Workshop.
 

### 2024-06-24 paper/paper-part1.tex
add title

--- 2024-06-24 paper/paper.tex
@@
-%% The first command in your LaTeX source must be the \documentclass command.
-%%
-%% Options:
-%% twocolumn : Two column layout.
-%% hf: enable header and footer.
-\documentclass[
-% twocolumn,
-% hf,
-]{ceurart}
-
-%%
-%% One can fix some overfulls
-\sloppy
-
-%%
-%% Minted listings support 
-%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
-\usepackage{listings}
-%% auto break lines
-\lstset{breaklines=true}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-
-%%
-%% Rights management information.
-%% CC-BY is default license.
-\copyrightyear{2022}
-\copyrightclause{Copyright for this paper by its authors.
-  Use permitted under Creative Commons License Attribution 4.0
-  International (CC BY 4.0).}
-
-%%
-%% This command is for the conference information
-\conference{Woodstock'22: Symposium on the irreproducible science,
-  June 07--11, 2022, Woodstock, NY}
-
-%%
-%% The "title" command
-\title{A better way to format your document for CEUR-WS}
-
-\tnotemark[1]
-\tnotetext[1]{You can use this document as the template for preparing your
-  publication. We recommend using the latest version of the ceurart style.}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-\author[1,2]{Dmitry S. Kulyabov}[%
-orcid=0000-0002-0877-7063,
-email=kulyabov-ds@rudn.ru,
-url=https://yamadharma.github.io/,
-]
-\cormark[1]
-\fnmark[1]
-\address[1]{Peoples' Friendship University of Russia (RUDN University),
-  6 Miklukho-Maklaya St, Moscow, 117198, Russian Federation}
-\address[2]{Joint Institute for Nuclear Research,
-  6 Joliot-Curie, Dubna, Moscow region, 141980, Russian Federation}
-
-\author[3]{Ilaria Tiddi}[%
-orcid=0000-0001-7116-9338,
-email=i.tiddi@vu.nl,
-url=https://kmitd.github.io/ilaria/,
-]
-\fnmark[1]
-\address[3]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}
-
-\author[4]{Manfred Jeusfeld}[%
-orcid=0000-0002-9421-8566,
-email=Manfred.Jeusfeld@acm.org,
-url=http://conceptbase.sourceforge.net/mjf/,
-]
-\fnmark[1]
-\address[4]{University of Skövde, Högskolevägen 1, 541 28 Skövde, Sweden}
-
-%% Footnotes
-\cortext[1]{Corresponding author.}
-\fntext[1]{These authors contributed equally.}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
-\begin{abstract}
-  A clear and well-documented \LaTeX{} document is presented as an
-  article formatted for publication by CEUR-WS in a conference
-  proceedings. Based on the ``ceurart'' document class, this article
-  presents and explains many of the common variations, as well as many
-  of the formatting elements an author may use in the preparation of
-  the documentation of their work.
-\end{abstract}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\begin{keywords}
-  LaTeX class \sep
-  paper template \sep
-  paper formatting \sep
-  CEUR-WS
-\end{keywords}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
 \section{Introduction}
@@
 We work towards a long-term vision for sustainable and effective neural information retrieval—themes and motivations that best fit the ReNeuIR Workshop.
-
-\input{paper-part2}
-
-The ``\verb|ceurart|'' document class can be used to prepare articles
-for any CEUR-WS publication, and for any stage of publication, from
-review to final ``camera-ready'' copy with {\itshape very} few changes
-to the source.
-
-This class depends on the following packages
-for its proper functioning:
-
-\begin{itemize}
-\item \verb|natbib.sty| for citation processing;
-\item \verb|geometry.sty| for margin settings;
-\item \verb|graphicx.sty| for graphics inclusion;
-\item \verb|hyperref.sty| optional package if hyperlinking is required in
-  the document;
-\item \verb|fontawesome5.sty| optional package for bells and whistles.
-\end{itemize}
-
-All the above packages are part of any
-standard \LaTeX{} installation.
-Therefore, the users need not be
-bothered about downloading any extra packages.
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-\section{Template parameters}
-
-There are a number of template
-parameters which modify some part of the \verb|ceurart| document class.
-This parameters are enclosed in square
-brackets and are a part of the \verb|\documentclass| command:
-\begin{lstlisting}
-  \documentclass[parameter]{ceurart}
-\end{lstlisting}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item \verb|twocolumn| : Two column layout.
-\item \verb|hf| : Enable header and footer\footnote{You can enable
-    the display of page numbers in the final version of the entire
-    collection. In this case, you should adhere to the end-to-end
-    pagination of individual papers.}.
-\end{itemize}
-
-\section{Front matter}
-
-\subsection{Title Information}
-
-The titles of papers should be either all use the emphasizing
-capitalized style or they should all use the regular English (or
-native language) style. It does not make a good impression if you or
-your authors mix the styles.
-
-Use the \verb|\title| command to define the title of your work. Do not
-insert line breaks in your title.
-
-\subsection{Title variants}
-
-\verb|\title| command have the below options:
-\begin{itemize}
-\item \verb|title|: Document title. This is default option. 
-\begin{lstlisting}
-\title[mode=title]{This is a title}
-\end{lstlisting}
-You can just omit it, like as follows:
-\begin{lstlisting}
-\title{This is a title}
-\end{lstlisting}
-
-\item \verb|alt|: Alternate title.
-\begin{lstlisting}
-\title[mode=alt]{This is a alternate title}
-\end{lstlisting}
-
-\item \verb|sub|: Sub title.
-\begin{lstlisting}
-\title[mode=sub]{This is a sub title}
-\end{lstlisting}
-You can just use \verb|\subtitle| command, as follows:
-\begin{lstlisting}
-\subtitle{This is a sub title}
-\end{lstlisting}
-
-\item \verb|trans|: Translated title.
-\begin{lstlisting}
-\title[mode=trans]{This is a translated title}
-\end{lstlisting}
-
-\item \verb|transsub|: Translated sub title.
-\begin{lstlisting}
-\title[mode=transsub]{This is a translated sub title}
-\end{lstlisting}
-\end{itemize}
-
-\subsection{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-\verb|\author| command have the below options:
-
-\begin{itemize}
-\item \verb|style| : Style of author name (chinese)
-\item \verb|prefix| : Prefix
-\item \verb|suffix| : Suffix
-\item \verb|degree| : Degree
-\item \verb|role| : Role
-\item \verb|orcid| : ORCID
-\item \verb|email| : E-mail
-\item \verb|url| : URL
-\end{itemize}
-
-Author names can have some kinds of marks and notes:
-\begin{itemize}
-\item affiliation mark: \verb|\author[<num>]|.
-\end{itemize}
-
-The author names and affiliations could be formatted in two ways:
-\begin{enumerate}
-\item Group the authors per affiliation.
-\item Use an explicit mark to indicate the affiliations.
-\end{enumerate}
-
-Author block example:
-\begin{lstlisting}
-\author[1,2]{Author Name}[%
-    prefix=Prof.,
-    degree=D.Sc.,
-    role=Researcher,
-    orcid=0000-0000-000-0000,
-    email=name@example.com,
-    url=https://name.example.com
-]
-
-\address[1]{Affiliation #1}
-\address[2]{Affiliation #2}
-\end{lstlisting}
-
-\subsection{Abstract and Keywords}
-
-Abstract shall be entered in an environment that starts
-with \verb|\begin{abstract}| and ends with
-\verb|\end{abstract}|.
-
-\begin{lstlisting}
-\begin{abstract}
-  This is an abstract.
-\end{abstract}
-\end{lstlisting}
-
-The key words are enclosed in a \verb|keywords|
-environment. Use \verb|\sep| to separate keywords.
-
-\begin{lstlisting}
-\begin{keywords}
-  First keyword \sep 
-  Second keyword \sep 
-  Third keyword \sep 
-  Fourth keyword
-\end{keywords}
-\end{lstlisting}
-
-At the end of front matter add \verb|\maketitle| command.
-
-\subsection{Various Marks in the Front Matter}
-
-The front matter becomes complicated due to various kinds
-of notes and marks to the title and author names. Marks in
-the title will be denoted by a star ($\star$) mark;
-footnotes are denoted by super scripted Arabic numerals,
-corresponding author by an Conformal asterisk (*) mark.
-
-\subsubsection{Title marks}
-
-Title mark can be entered by the command, \verb|\tnotemark[<num>]|
-and the corresponding text can be entered with the command
-\verb|\tnotetext[<num>]{<text>}|. An example will be:
-
-\begin{lstlisting}
-\title{A better way to format your document for CEUR-WS}
-
-\tnotemark[1]
-\tnotetext[1]{You can use this document as the template for preparing your
-  publication. We recommend using the latest version of the ceurart style.}
-\end{lstlisting}
-
-\verb|\tnotemark| and \verb|\tnotetext| can be anywhere in
-the front matter, but should be before \verb|\maketitle| command.
-
-\subsubsection{Author marks}
-
-Author names can have some kinds of marks and notes:
-\begin{itemize}
-\item footnote mark : \verb|\fnmark[<num>]|
-\item footnote text : \verb|\fntext[<num>]{<text>}|
-\item corresponding author mark : \verb|\cormark[<num>]|
-\item corresponding author text : \verb|\cortext[<num>]{<text>}|
-\end{itemize}
-
-\subsubsection{Other marks}
-
-At times, authors want footnotes which leave no marks in
-the author names. The note text shall be listed as part of
-the front matter notes. Class files provides
-\verb|\nonumnote| for this purpose. The usage
-\begin{lstlisting}
-\nonumnote{<text>}
-\end{lstlisting}
-and should be entered anywhere before the \verb|\maketitle|
-command for this to take effect.
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX{} sectioning commands:
-\verb|\section|, \verb|\subsection|,
-\verb|\subsubsection|, and
-\verb|\paragraph|. They should be numbered; do not remove
-the numbering from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is not allowed.
-
-\section{Tables}
-
-The ``\verb|ceurart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed \textit{above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \verb|table| to enclose the table's contents and the
-table caption. The contents of the table itself must go in the
-\verb|tabular| environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table*}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table*}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \verb|table*| to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Math Equations}
-
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \verb|math| environment,
-which can be invoked with the usual
-\verb|\begin| \ldots \verb|\end| construction or with
-the short form \verb|$| \ldots \verb|$|. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX
-this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty} \frac{1}{n} = 0,
-\end{math}
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \verb|equation|
-environment. An unnumbered display equation is produced by the
-\verb|displaymath| environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX{}; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty} \frac{1}{n} = 0.
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \verb|displaymath|
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  S_{n} = \sum_{i=1}^{n} x_{i} ,
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \lim_{x \to 0} (1 + x)^{1/x} = e
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-also include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed below the figure.
-
-\section{Citations and Bibliographies}
-
-The use of Bib\TeX{} for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}|
-command:
-\begin{lstlisting}
-\bibliography{bibfile}
-\end{lstlisting}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the Bib\TeX{} file.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{lstlisting}
-\begin{acknowledgments}
-  These are different acknowledgments.
-\end{acknowledgments}
-\end{lstlisting}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered
-\verb|\section|; please use the ``\verb|acknowledgments|'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|\appendix|'' command:
-\begin{lstlisting}
-\appendix
-\end{lstlisting}
-and note that in the appendix, sections are lettered, not
-numbered.
-
-%%
-%% The acknowledgments section is defined using the "acknowledgments" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acknowledgments}
-  Thanks to the developers of ACM consolidated LaTeX styles
-  \url{https://github.com/borisveytsman/acmart} and to the developers
-  of Elsevier updated \LaTeX{} templates
-  \url{https://www.ctan.org/tex-archive/macros/latex/contrib/els-cas-templates}.  
-\end{acknowledgments}
-
-%%
-%% Define the bibliography file to be used
-\bibliography{sample-ceur}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Online Resources}
-
-The sources for the ceur-art style are available via
-\begin{itemize}
-\item \href{https://github.com/yamadharma/ceurart}{GitHub},
-% \item \href{https://www.overleaf.com/project/5e76702c4acae70001d3bc87}{Overleaf},
-\item
-  \href{https://www.overleaf.com/latex/templates/template-for-submissions-to-ceur-workshop-proceedings-ceur-ws-dot-org/pkfscdkgkhcq}{Overleaf
-    template}.
-\end{itemize}
-
-\end{document}
-
-%%
-%% End of file

### 2024-06-24 paper/paper-pre.tex
add title

--- 2024-04-22 paper/paper.tex
@@
-%% The first command in your LaTeX source must be the \documentclass command.
-%%
-%% Options:
-%% twocolumn : Two column layout.
-%% hf: enable header and footer.
-\documentclass[
-% twocolumn,
-% hf,
-]{ceurart}
-
-%%
-%% One can fix some overfulls
-\sloppy
-
-%%
-%% Minted listings support 
-%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
-\usepackage{listings}
-%% auto break lines
-\lstset{breaklines=true}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
+\title{Team FSU at ReNeuIR 2024}
+\subtitle{Document Re-Ranking with Tiny Cross Encoders}
+%\subtitle{Does it work with TinyBERT? Testing X,y and Z for xxyyx.}
 
@@
 %% CC-BY is default license.
-\copyrightyear{2022}
+\copyrightyear{2024}
 \copyrightclause{Copyright for this paper by its authors.
@@
   June 07--11, 2022, Woodstock, NY}
-
-%%
-%% The "title" command
-\title{A better way to format your document for CEUR-WS}
 
@@
 \maketitle
-
-\section{Introduction}
-
-CEUR-WS's article template provides a consistent \LaTeX{} style for
-use across CEUR-WS publications, and incorporates accessibility and
-metadata-extraction functionality. This document will explain the
-major features of the document class.
-
-If you are new to publishing with CEUR-WS, this document is a valuable
-guide to the process of preparing your work for publication.
-
-\input{paper-part2}
-
-The ``\verb|ceurart|'' document class can be used to prepare articles
-for any CEUR-WS publication, and for any stage of publication, from
-review to final ``camera-ready'' copy with {\itshape very} few changes
-to the source.
-
-This class depends on the following packages
-for its proper functioning:
-
-\begin{itemize}
-\item \verb|natbib.sty| for citation processing;
-\item \verb|geometry.sty| for margin settings;
-\item \verb|graphicx.sty| for graphics inclusion;
-\item \verb|hyperref.sty| optional package if hyperlinking is required in
-  the document;
-\item \verb|fontawesome5.sty| optional package for bells and whistles.
-\end{itemize}
-
-All the above packages are part of any
-standard \LaTeX{} installation.
-Therefore, the users need not be
-bothered about downloading any extra packages.
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-\section{Template parameters}
-
-There are a number of template
-parameters which modify some part of the \verb|ceurart| document class.
-This parameters are enclosed in square
-brackets and are a part of the \verb|\documentclass| command:
-\begin{lstlisting}
-  \documentclass[parameter]{ceurart}
-\end{lstlisting}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item \verb|twocolumn| : Two column layout.
-\item \verb|hf| : Enable header and footer\footnote{You can enable
-    the display of page numbers in the final version of the entire
-    collection. In this case, you should adhere to the end-to-end
-    pagination of individual papers.}.
-\end{itemize}
-
-\section{Front matter}
-
-\subsection{Title Information}
-
-The titles of papers should be either all use the emphasizing
-capitalized style or they should all use the regular English (or
-native language) style. It does not make a good impression if you or
-your authors mix the styles.
-
-Use the \verb|\title| command to define the title of your work. Do not
-insert line breaks in your title.
-
-\subsection{Title variants}
-
-\verb|\title| command have the below options:
-\begin{itemize}
-\item \verb|title|: Document title. This is default option. 
-\begin{lstlisting}
-\title[mode=title]{This is a title}
-\end{lstlisting}
-You can just omit it, like as follows:
-\begin{lstlisting}
-\title{This is a title}
-\end{lstlisting}
-
-\item \verb|alt|: Alternate title.
-\begin{lstlisting}
-\title[mode=alt]{This is a alternate title}
-\end{lstlisting}
-
-\item \verb|sub|: Sub title.
-\begin{lstlisting}
-\title[mode=sub]{This is a sub title}
-\end{lstlisting}
-You can just use \verb|\subtitle| command, as follows:
-\begin{lstlisting}
-\subtitle{This is a sub title}
-\end{lstlisting}
-
-\item \verb|trans|: Translated title.
-\begin{lstlisting}
-\title[mode=trans]{This is a translated title}
-\end{lstlisting}
-
-\item \verb|transsub|: Translated sub title.
-\begin{lstlisting}
-\title[mode=transsub]{This is a translated sub title}
-\end{lstlisting}
-\end{itemize}
-
-\subsection{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-\verb|\author| command have the below options:
-
-\begin{itemize}
-\item \verb|style| : Style of author name (chinese)
-\item \verb|prefix| : Prefix
-\item \verb|suffix| : Suffix
-\item \verb|degree| : Degree
-\item \verb|role| : Role
-\item \verb|orcid| : ORCID
-\item \verb|email| : E-mail
-\item \verb|url| : URL
-\end{itemize}
-
-Author names can have some kinds of marks and notes:
-\begin{itemize}
-\item affiliation mark: \verb|\author[<num>]|.
-\end{itemize}
-
-The author names and affiliations could be formatted in two ways:
-\begin{enumerate}
-\item Group the authors per affiliation.
-\item Use an explicit mark to indicate the affiliations.
-\end{enumerate}
-
-Author block example:
-\begin{lstlisting}
-\author[1,2]{Author Name}[%
-    prefix=Prof.,
-    degree=D.Sc.,
-    role=Researcher,
-    orcid=0000-0000-000-0000,
-    email=name@example.com,
-    url=https://name.example.com
-]
-
-\address[1]{Affiliation #1}
-\address[2]{Affiliation #2}
-\end{lstlisting}
-
-\subsection{Abstract and Keywords}
-
-Abstract shall be entered in an environment that starts
-with \verb|\begin{abstract}| and ends with
-\verb|\end{abstract}|.
-
-\begin{lstlisting}
-\begin{abstract}
-  This is an abstract.
-\end{abstract}
-\end{lstlisting}
-
-The key words are enclosed in a \verb|keywords|
-environment. Use \verb|\sep| to separate keywords.
-
-\begin{lstlisting}
-\begin{keywords}
-  First keyword \sep 
-  Second keyword \sep 
-  Third keyword \sep 
-  Fourth keyword
-\end{keywords}
-\end{lstlisting}
-
-At the end of front matter add \verb|\maketitle| command.
-
-\subsection{Various Marks in the Front Matter}
-
-The front matter becomes complicated due to various kinds
-of notes and marks to the title and author names. Marks in
-the title will be denoted by a star ($\star$) mark;
-footnotes are denoted by super scripted Arabic numerals,
-corresponding author by an Conformal asterisk (*) mark.
-
-\subsubsection{Title marks}
-
-Title mark can be entered by the command, \verb|\tnotemark[<num>]|
-and the corresponding text can be entered with the command
-\verb|\tnotetext[<num>]{<text>}|. An example will be:
-
-\begin{lstlisting}
-\title{A better way to format your document for CEUR-WS}
-
-\tnotemark[1]
-\tnotetext[1]{You can use this document as the template for preparing your
-  publication. We recommend using the latest version of the ceurart style.}
-\end{lstlisting}
-
-\verb|\tnotemark| and \verb|\tnotetext| can be anywhere in
-the front matter, but should be before \verb|\maketitle| command.
-
-\subsubsection{Author marks}
-
-Author names can have some kinds of marks and notes:
-\begin{itemize}
-\item footnote mark : \verb|\fnmark[<num>]|
-\item footnote text : \verb|\fntext[<num>]{<text>}|
-\item corresponding author mark : \verb|\cormark[<num>]|
-\item corresponding author text : \verb|\cortext[<num>]{<text>}|
-\end{itemize}
-
-\subsubsection{Other marks}
-
-At times, authors want footnotes which leave no marks in
-the author names. The note text shall be listed as part of
-the front matter notes. Class files provides
-\verb|\nonumnote| for this purpose. The usage
-\begin{lstlisting}
-\nonumnote{<text>}
-\end{lstlisting}
-and should be entered anywhere before the \verb|\maketitle|
-command for this to take effect.
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX{} sectioning commands:
-\verb|\section|, \verb|\subsection|,
-\verb|\subsubsection|, and
-\verb|\paragraph|. They should be numbered; do not remove
-the numbering from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is not allowed.
-
-\section{Tables}
-
-The ``\verb|ceurart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed \textit{above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \verb|table| to enclose the table's contents and the
-table caption. The contents of the table itself must go in the
-\verb|tabular| environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table*}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table*}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \verb|table*| to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Math Equations}
-
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \verb|math| environment,
-which can be invoked with the usual
-\verb|\begin| \ldots \verb|\end| construction or with
-the short form \verb|$| \ldots \verb|$|. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX
-this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty} \frac{1}{n} = 0,
-\end{math}
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \verb|equation|
-environment. An unnumbered display equation is produced by the
-\verb|displaymath| environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX{}; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty} \frac{1}{n} = 0.
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \verb|displaymath|
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  S_{n} = \sum_{i=1}^{n} x_{i} ,
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \lim_{x \to 0} (1 + x)^{1/x} = e
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-also include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed below the figure.
-
-\section{Citations and Bibliographies}
-
-The use of Bib\TeX{} for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}|
-command:
-\begin{lstlisting}
-\bibliography{bibfile}
-\end{lstlisting}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the Bib\TeX{} file.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{lstlisting}
-\begin{acknowledgments}
-  These are different acknowledgments.
-\end{acknowledgments}
-\end{lstlisting}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered
-\verb|\section|; please use the ``\verb|acknowledgments|'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|\appendix|'' command:
-\begin{lstlisting}
-\appendix
-\end{lstlisting}
-and note that in the appendix, sections are lettered, not
-numbered.
-
-%%
-%% The acknowledgments section is defined using the "acknowledgments" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acknowledgments}
-  Thanks to the developers of ACM consolidated LaTeX styles
-  \url{https://github.com/borisveytsman/acmart} and to the developers
-  of Elsevier updated \LaTeX{} templates
-  \url{https://www.ctan.org/tex-archive/macros/latex/contrib/els-cas-templates}.  
-\end{acknowledgments}
-
-%%
-%% Define the bibliography file to be used
-\bibliography{sample-ceur}
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Online Resources}
-
-The sources for the ceur-art style are available via
-\begin{itemize}
-\item \href{https://github.com/yamadharma/ceurart}{GitHub},
-% \item \href{https://www.overleaf.com/project/5e76702c4acae70001d3bc87}{Overleaf},
-\item
-  \href{https://www.overleaf.com/latex/templates/template-for-submissions-to-ceur-workshop-proceedings-ceur-ws-dot-org/pkfscdkgkhcq}{Overleaf
-    template}.
-\end{itemize}
-
-\end{document}
-
-%%
-%% End of file

### 2024-06-24 paper/paper.tex
add title

--- 2024-04-22 paper/paper.tex
@@
 
-%%
-%% Rights management information.
-%% CC-BY is default license.
-\copyrightyear{2022}
-\copyrightclause{Copyright for this paper by its authors.
-  Use permitted under Creative Commons License Attribution 4.0
-  International (CC BY 4.0).}
-
-%%
-%% This command is for the conference information
-\conference{Woodstock'22: Symposium on the irreproducible science,
-  June 07--11, 2022, Woodstock, NY}
-
-%%
-%% The "title" command
-\title{A better way to format your document for CEUR-WS}
-
-\tnotemark[1]
-\tnotetext[1]{You can use this document as the template for preparing your
-  publication. We recommend using the latest version of the ceurart style.}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-\author[1,2]{Dmitry S. Kulyabov}[%
-orcid=0000-0002-0877-7063,
-email=kulyabov-ds@rudn.ru,
-url=https://yamadharma.github.io/,
-]
-\cormark[1]
-\fnmark[1]
-\address[1]{Peoples' Friendship University of Russia (RUDN University),
-  6 Miklukho-Maklaya St, Moscow, 117198, Russian Federation}
-\address[2]{Joint Institute for Nuclear Research,
-  6 Joliot-Curie, Dubna, Moscow region, 141980, Russian Federation}
-
-\author[3]{Ilaria Tiddi}[%
-orcid=0000-0001-7116-9338,
-email=i.tiddi@vu.nl,
-url=https://kmitd.github.io/ilaria/,
-]
-\fnmark[1]
-\address[3]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}
-
-\author[4]{Manfred Jeusfeld}[%
-orcid=0000-0002-9421-8566,
-email=Manfred.Jeusfeld@acm.org,
-url=http://conceptbase.sourceforge.net/mjf/,
-]
-\fnmark[1]
-\address[4]{University of Skövde, Högskolevägen 1, 541 28 Skövde, Sweden}
-
-%% Footnotes
-\cortext[1]{Corresponding author.}
-\fntext[1]{These authors contributed equally.}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
-\begin{abstract}
-  A clear and well-documented \LaTeX{} document is presented as an
-  article formatted for publication by CEUR-WS in a conference
-  proceedings. Based on the ``ceurart'' document class, this article
-  presents and explains many of the common variations, as well as many
-  of the formatting elements an author may use in the preparation of
-  the documentation of their work.
-\end{abstract}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\begin{keywords}
-  LaTeX class \sep
-  paper template \sep
-  paper formatting \sep
-  CEUR-WS
-\end{keywords}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
-\section{Introduction}
-
-CEUR-WS's article template provides a consistent \LaTeX{} style for
-use across CEUR-WS publications, and incorporates accessibility and
-metadata-extraction functionality. This document will explain the
-major features of the document class.
-
-If you are new to publishing with CEUR-WS, this document is a valuable
-guide to the process of preparing your work for publication.
+\input{paper-pre}
+\input{paper-part1}
 
 \input{paper-part2}
-
-The ``\verb|ceurart|'' document class can be used to prepare articles
-for any CEUR-WS publication, and for any stage of publication, from
-review to final ``camera-ready'' copy with {\itshape very} few changes
-to the source.
-
-This class depends on the following packages
-for its proper functioning:
-
-\begin{itemize}
-\item \verb|natbib.sty| for citation processing;
-\item \verb|geometry.sty| for margin settings;
-\item \verb|graphicx.sty| for graphics inclusion;
-\item \verb|hyperref.sty| optional package if hyperlinking is required in
-  the document;
-\item \verb|fontawesome5.sty| optional package for bells and whistles.
-\end{itemize}
-
-All the above packages are part of any
-standard \LaTeX{} installation.
-Therefore, the users need not be
-bothered about downloading any extra packages.
-
-\section{Modifications}
-
-Modifying the template --- including but not limited to: adjusting
-margins, typeface sizes, line spacing, paragraph and list definitions,
-and the use of the \verb|\vspace| command to manually adjust the
-vertical spacing between elements of your work --- is not allowed.
-
-\section{Template parameters}
-
-There are a number of template
-parameters which modify some part of the \verb|ceurart| document class.
-This parameters are enclosed in square
-brackets and are a part of the \verb|\documentclass| command:
-\begin{lstlisting}
-  \documentclass[parameter]{ceurart}
-\end{lstlisting}
-
-Frequently-used parameters, or combinations of parameters, include:
-\begin{itemize}
-\item \verb|twocolumn| : Two column layout.
-\item \verb|hf| : Enable header and footer\footnote{You can enable
-    the display of page numbers in the final version of the entire
-    collection. In this case, you should adhere to the end-to-end
-    pagination of individual papers.}.
-\end{itemize}
-
-\section{Front matter}
-
-\subsection{Title Information}
-
-The titles of papers should be either all use the emphasizing
-capitalized style or they should all use the regular English (or
-native language) style. It does not make a good impression if you or
-your authors mix the styles.
-
-Use the \verb|\title| command to define the title of your work. Do not
-insert line breaks in your title.
-
-\subsection{Title variants}
-
-\verb|\title| command have the below options:
-\begin{itemize}
-\item \verb|title|: Document title. This is default option. 
-\begin{lstlisting}
-\title[mode=title]{This is a title}
-\end{lstlisting}
-You can just omit it, like as follows:
-\begin{lstlisting}
-\title{This is a title}
-\end{lstlisting}
-
-\item \verb|alt|: Alternate title.
-\begin{lstlisting}
-\title[mode=alt]{This is a alternate title}
-\end{lstlisting}
-
-\item \verb|sub|: Sub title.
-\begin{lstlisting}
-\title[mode=sub]{This is a sub title}
-\end{lstlisting}
-You can just use \verb|\subtitle| command, as follows:
-\begin{lstlisting}
-\subtitle{This is a sub title}
-\end{lstlisting}
-
-\item \verb|trans|: Translated title.
-\begin{lstlisting}
-\title[mode=trans]{This is a translated title}
-\end{lstlisting}
-
-\item \verb|transsub|: Translated sub title.
-\begin{lstlisting}
-\title[mode=transsub]{This is a translated sub title}
-\end{lstlisting}
-\end{itemize}
-
-\subsection{Authors and Affiliations}
-
-Each author must be defined separately for accurate metadata
-identification. Multiple authors may share one affiliation. Authors'
-names should not be abbreviated; use full first names wherever
-possible. Include authors' e-mail addresses whenever possible.
-
-\verb|\author| command have the below options:
-
-\begin{itemize}
-\item \verb|style| : Style of author name (chinese)
-\item \verb|prefix| : Prefix
-\item \verb|suffix| : Suffix
-\item \verb|degree| : Degree
-\item \verb|role| : Role
-\item \verb|orcid| : ORCID
-\item \verb|email| : E-mail
-\item \verb|url| : URL
-\end{itemize}
-
-Author names can have some kinds of marks and notes:
-\begin{itemize}
-\item affiliation mark: \verb|\author[<num>]|.
-\end{itemize}
-
-The author names and affiliations could be formatted in two ways:
-\begin{enumerate}
-\item Group the authors per affiliation.
-\item Use an explicit mark to indicate the affiliations.
-\end{enumerate}
-
-Author block example:
-\begin{lstlisting}
-\author[1,2]{Author Name}[%
-    prefix=Prof.,
-    degree=D.Sc.,
-    role=Researcher,
-    orcid=0000-0000-000-0000,
-    email=name@example.com,
-    url=https://name.example.com
-]
-
-\address[1]{Affiliation #1}
-\address[2]{Affiliation #2}
-\end{lstlisting}
-
-\subsection{Abstract and Keywords}
-
-Abstract shall be entered in an environment that starts
-with \verb|\begin{abstract}| and ends with
-\verb|\end{abstract}|.
-
-\begin{lstlisting}
-\begin{abstract}
-  This is an abstract.
-\end{abstract}
-\end{lstlisting}
-
-The key words are enclosed in a \verb|keywords|
-environment. Use \verb|\sep| to separate keywords.
-
-\begin{lstlisting}
-\begin{keywords}
-  First keyword \sep 
-  Second keyword \sep 
-  Third keyword \sep 
-  Fourth keyword
-\end{keywords}
-\end{lstlisting}
-
-At the end of front matter add \verb|\maketitle| command.
-
-\subsection{Various Marks in the Front Matter}
-
-The front matter becomes complicated due to various kinds
-of notes and marks to the title and author names. Marks in
-the title will be denoted by a star ($\star$) mark;
-footnotes are denoted by super scripted Arabic numerals,
-corresponding author by an Conformal asterisk (*) mark.
-
-\subsubsection{Title marks}
-
-Title mark can be entered by the command, \verb|\tnotemark[<num>]|
-and the corresponding text can be entered with the command
-\verb|\tnotetext[<num>]{<text>}|. An example will be:
-
-\begin{lstlisting}
-\title{A better way to format your document for CEUR-WS}
-
-\tnotemark[1]
-\tnotetext[1]{You can use this document as the template for preparing your
-  publication. We recommend using the latest version of the ceurart style.}
-\end{lstlisting}
-
-\verb|\tnotemark| and \verb|\tnotetext| can be anywhere in
-the front matter, but should be before \verb|\maketitle| command.
-
-\subsubsection{Author marks}
-
-Author names can have some kinds of marks and notes:
-\begin{itemize}
-\item footnote mark : \verb|\fnmark[<num>]|
-\item footnote text : \verb|\fntext[<num>]{<text>}|
-\item corresponding author mark : \verb|\cormark[<num>]|
-\item corresponding author text : \verb|\cortext[<num>]{<text>}|
-\end{itemize}
-
-\subsubsection{Other marks}
-
-At times, authors want footnotes which leave no marks in
-the author names. The note text shall be listed as part of
-the front matter notes. Class files provides
-\verb|\nonumnote| for this purpose. The usage
-\begin{lstlisting}
-\nonumnote{<text>}
-\end{lstlisting}
-and should be entered anywhere before the \verb|\maketitle|
-command for this to take effect.
-
-\section{Sectioning Commands}
-
-Your work should use standard \LaTeX{} sectioning commands:
-\verb|\section|, \verb|\subsection|,
-\verb|\subsubsection|, and
-\verb|\paragraph|. They should be numbered; do not remove
-the numbering from the commands.
-
-Simulating a sectioning command by setting the first word or words of
-a paragraph in boldface or italicized text is not allowed.
-
-\section{Tables}
-
-The ``\verb|ceurart|'' document class includes the ``\verb|booktabs|''
-package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
-high-quality tables.
-
-Table captions are placed \textit{above} the table.
-
-Because tables cannot be split across pages, the best placement for
-them is typically the top of the page nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \verb|table| to enclose the table's contents and the
-table caption. The contents of the table itself must go in the
-\verb|tabular| environment, to be aligned properly in rows and
-columns, with the desired horizontal and vertical rules.
-
-Immediately following this sentence is the point at which
-Table~\ref{tab:freq} is included in the input file; compare the
-placement of the table here with the table in the printed output of
-this document.
-
-\begin{table*}
-  \caption{Frequency of Special Characters}
-  \label{tab:freq}
-  \begin{tabular}{ccl}
-    \toprule
-    Non-English or Math&Frequency&Comments\\
-    \midrule
-    \O & 1 in 1,000& For Swedish names\\
-    $\pi$ & 1 in 5& Common in math\\
-    \$ & 4 in 5 & Used in business\\
-    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-  \bottomrule
-\end{tabular}
-\end{table*}
-
-To set a wider table, which takes up the whole width of the page's
-live area, use the environment \verb|table*| to enclose the table's
-contents and the table caption.  As with a single-column table, this
-wide table will ``float'' to a location deemed more
-desirable. Immediately following this sentence is the point at which
-Table~\ref{tab:commands} is included in the input file; again, it is
-instructive to compare the placement of the table here with the table
-in the printed output of this document.
-
-\begin{table}
-  \caption{Some Typical Commands}
-  \label{tab:commands}
-  \begin{tabular}{ccl}
-    \toprule
-    Command &A Number & Comments\\
-    \midrule
-    \texttt{{\char'134}author} & 100& Author \\
-    \texttt{{\char'134}table}& 300 & For tables\\
-    \texttt{{\char'134}table*}& 400& For wider tables\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Math Equations}
-
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of the three are
-discussed in the next sections.
-
-\subsection{Inline (In-text) Equations}
-
-A formula that appears in the running text is called an inline or
-in-text formula.  It is produced by the \verb|math| environment,
-which can be invoked with the usual
-\verb|\begin| \ldots \verb|\end| construction or with
-the short form \verb|$| \ldots \verb|$|. You can use any of the symbols
-and structures, from $\alpha$ to $\omega$, available in
-\LaTeX
-this section will simply show a few
-examples of in-text equations in context. Notice how this equation:
-\begin{math}
-  \lim_{n\rightarrow \infty} \frac{1}{n} = 0,
-\end{math}
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsection{Display Equations}
-
-A numbered display equation---one set off by vertical space from the
-text and centered horizontally---is produced by the \verb|equation|
-environment. An unnumbered display equation is produced by the
-\verb|displaymath| environment.
-
-Again, in either environment, you can use any of the symbols and
-structures available in \LaTeX{}; this section will just give a couple
-of examples of display equations in context.  First, consider the
-equation, shown as an inline equation above:
-\begin{equation}
-  \lim_{n\rightarrow \infty} \frac{1}{n} = 0.
-\end{equation}
-Notice how it is formatted somewhat differently in
-the \verb|displaymath|
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}
-  S_{n} = \sum_{i=1}^{n} x_{i} ,
-\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}
-  \lim_{x \to 0} (1 + x)^{1/x} = e
-\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\section{Figures}
-
-The ``\verb|figure|'' environment should be used for figures. One or
-more images can be placed within a figure. If your figure contains
-third-party material, you must clearly identify it as such, as shown
-in the example below.
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{sample-franklin}
-  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
-    Ewing, Inc. [Public domain], via Wikimedia
-    Commons. (\url{https://goo.gl/VLCRBB}).}
-\end{figure}
-
-Your figures should contain a caption which describes the figure to
-the reader. Figure captions go below the figure. Your figures should
-also include a description suitable for screen readers, to
-assist the visually-challenged to better understand your work.
-
-Figure captions are placed below the figure.
-
-\section{Citations and Bibliographies}
-
-The use of Bib\TeX{} for the preparation and formatting of one's
-references is strongly recommended. Authors' names should be complete
---- use full first names (``Donald E. Knuth'') not initials
-(``D. E. Knuth'') --- and the salient identifying features of a
-reference should be included: title, year, volume, number, pages,
-article DOI, etc.
-
-The bibliography is included in your source document with these two
-commands, placed just before the \verb|\end{document}|
-command:
-\begin{lstlisting}
-\bibliography{bibfile}
-\end{lstlisting}
-where ``\verb|bibfile|'' is the name, without the ``\verb|.bib|''
-suffix, of the Bib\TeX{} file.
-
-\section{Acknowledgments}
-
-Identification of funding sources and other support, and thanks to
-individuals and groups that assisted in the research and the
-preparation of the work should be included in an acknowledgment
-section, which is placed just before the reference section in your
-document.
-
-This section has a special environment:
-\begin{lstlisting}
-\begin{acknowledgments}
-  These are different acknowledgments.
-\end{acknowledgments}
-\end{lstlisting}
-so that the information contained therein can be more easily collected
-during the article metadata extraction phase, and to ensure
-consistency in the spelling of the section heading.
-
-Authors should not prepare this section as a numbered or unnumbered
-\verb|\section|; please use the ``\verb|acknowledgments|'' environment.
-
-\section{Appendices}
-
-If your work needs an appendix, add it before the
-``\verb|\end{document}|'' command at the conclusion of your source
-document.
-
-Start the appendix with the ``\verb|\appendix|'' command:
-\begin{lstlisting}
-\appendix
-\end{lstlisting}
-and note that in the appendix, sections are lettered, not
-numbered.
-
-%%
-%% The acknowledgments section is defined using the "acknowledgments" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-\begin{acknowledgments}
-  Thanks to the developers of ACM consolidated LaTeX styles
-  \url{https://github.com/borisveytsman/acmart} and to the developers
-  of Elsevier updated \LaTeX{} templates
-  \url{https://www.ctan.org/tex-archive/macros/latex/contrib/els-cas-templates}.  
-\end{acknowledgments}
 
@@
 
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
-
-\section{Online Resources}
-
-The sources for the ceur-art style are available via
-\begin{itemize}
-\item \href{https://github.com/yamadharma/ceurart}{GitHub},
-% \item \href{https://www.overleaf.com/project/5e76702c4acae70001d3bc87}{Overleaf},
-\item
-  \href{https://www.overleaf.com/latex/templates/template-for-submissions-to-ceur-workshop-proceedings-ceur-ws-dot-org/pkfscdkgkhcq}{Overleaf
-    template}.
-\end{itemize}
-
 \end{document}
-
-%%
-%% End of file

### 2024-06-24 paper/paper-pre.tex
mf

@@
 \begin{abstract}
-  A clear and well-documented \LaTeX{} document is presented as an
-  article formatted for publication by CEUR-WS in a conference
-  proceedings. Based on the ``ceurart'' document class, this article
-  presents and explains many of the common variations, as well as many
-  of the formatting elements an author may use in the preparation of
-  the documentation of their work.
+% General Statement
+% - distillation +/- score injection improve cross-encoder
+%
+% Specific Problem
+% - unclear, if the two approaches transfer to tiny/smaller models
+% Outline proposed solution
+% Transfer two approaches to TinyBERT
+%
+% Evaluation: clear
+%
+  We describe the submission of team FSU in the ReNeuIR~2024 shared task on reaching efficiency in neural information retrieval.
+Previous work has shown that distillation and score injection are two approaches to make cross-encoders more effective.
+Still, the cross-encoders used in this previous works were rather big and hence not the most ``efficient'' ones.
+try to transfer two techniques that help to improve the effectiveness of cross-encoders to tiny models.
+We transfer {\color{red} ...}.
+Our experiments show {\color{red}...}.
+%
 \end{abstract}
@@
 \begin{keywords}
-  LaTeX class \sep
-  paper template \sep
-  paper formatting \sep
-  CEUR-WS
+  Tiny Cross Encoder \sep
+  Efficient Re-Ranking \sep
+  Distillation \sep
+  BM25 Score Injection
 \end{keywords}

### 2024-06-24 paper/paper-part3.tex
mf

\section{TinyBERT for Passage Re-Ranking on MS~MARCO}

\subsection{Plain TinyBERT}

\subsection{Distilling RankZephyr into TinyBERT}

\subsection{BM25 Score Injection for TinyBERT}

### 2024-06-24 paper/paper-part3.tex
doc: continued paper 3.1 and 3.3

@@
 
-\subsection{Plain TinyBERT}
+This section will introduce three approaches for training models for page reranking.
+First, we will train the plain TinyBERT model.
+Next, we will discuss the distillation process, and finally, we will cover the BM25 score injection method.
+
+\subsection{Plain training on TinyBERT}\label{plaintiny}
+% \subsection{Hyperparameter search on TinyBERT}
+% \subsection{Research on plain TinyBERT}
+
+In our first approach we trained the TinyBERT model by conducting a comprehensive hyperparameter search, systematically adjusting parameters.
+For comparison purposes, we initially defined a baseline with a batch size of $32$, $10$ epochs, and a learning rate of $2\mathrm{e}{-5}$.
+The variants we trained are listed in {\color{red} TABLE 1}.
+The dataset we used for this training was an extracted version of the MS MARCO Train Triples Small passage ranking dataset, containing approximately 8 million data samples.
+
+We later used an existing script designed for training models with BM25 score injection.
+To ensure consistency, we applied the same script for TinyBERT training, but without injecting any scores.
+This strategy was crucial as it allowed us to compare TinyBERT directly with other models trained on the same dataset, ensuring that any performance differences could be attributed to the model architectures rather than variations in the training process.
+The dataset used with the BM25 score injection script also contained approximately 8 million data samples from the MS MARCO Train Triples Small passage ranking dataset.
+This methodical approach facilitated a robust evaluation of TinyBERT's performance relative to other models trained under identical conditions.
 
@@
 
+{\color{red} Wer macht das?}
+
 \subsection{BM25 Score Injection for TinyBERT}
+
+To implement BM25 score injection, we referenced the paper \cite{askari23} to understand the methodology thoroughly.
+Finding their training script effective, we adopted it for our experiments.
+We conducted training using multiple variants: one with BM25 injection on the non-pretrained TinyBERT and another on the pretrained TinyBERT trained on the 1GB dataset which we introduced in section \hyperref[plaintiny]{Plain training on TinyBERT}.
+To prevent overfitting, we implemented an additional version for BM25 injection that includes early stopping.
+This involved integrating logic into our Cross Encoder, which assesses the model's performance during each evaluation phase.
+Specifically, it checks if the model achieves results at least as good as 99.5\% of its best performance so far.
+If this criterion isn't met consecutively three times, the training process stops automatically.
+This approach ensured that our models were trained efficiently and effectively, as described earlier.

### 2024-06-25 code/run-all-plain-tiny-models-on-validation-dataset.sh
mf

@@ -1,0 +1,18 @@
+#!/usr/bin/bash
+
+DIR="/mnt/ceph/storage/data-in-progress/data-research/web-search/RENEUIR-24/models-bm25-cat/fine-tuned/"
+
+for MODEL in $(find ${DIR} -name '*cross-encoder*' | awk -F '/' '{print $11}')
+do
+	echo "Run predictions with ${MODEL}"
+	docker run --rm -ti \
+	    --network=none \
+	    -v ${PWD}/lightning-ir/msmarco-dev/:/input-data:ro \
+	    -v ${PWD}/output-runs-tiny-bert-plain/${MODEL}:/runs \
+	    -v ${DIR}/${MODEL}/:/model \
+	    -e MODEL=/model \
+	    -e CUDA_VISIBLE_DEVICES=0 \
+	    -e TIRA_INPUT_DATASET=/input-data \
+	    -e TIRA_OUTPUT_DIR=/runs \
+	    tinybert-plain:0.0.1
+done

### 2024-06-25 code/run-all-with-injection-early-stopping-models-on-validation-dataset.sh
mf

@@ -1,0 +1,18 @@
+#!/usr/bin/bash
+
+DIR="/mnt/ceph/storage/data-in-progress/data-research/web-search/RENEUIR-24/models-bm25-cat/bm25-early-stopping-24-06-14_0995/"
+
+for MODEL in $(find ${DIR} -name '*cross-encoder*' | awk -F '/' '{print $11}')
+do
+	echo "Run predictions with ${MODEL}"
+	docker run --rm -ti \
+	    --network=none \
+	    -v ${PWD}/lightning-ir/msmarco-dev/:/input-data:ro \
+	    -v ${PWD}/output-runs-with-injection-and-early-stopping/${MODEL}:/runs \
+	    -v ${DIR}/${MODEL}/:/model \
+	    -e MODEL=/model \
+	    -e CUDA_VISIBLE_DEVICES=3 \
+	    -e TIRA_INPUT_DATASET=/input-data \
+	    -e TIRA_OUTPUT_DIR=/runs \
+	    tinybert-catbm25:0.0.1
+done

### 2024-06-26 code/lightning-ir/run-all-models-on-validation-dataset.sh
mf

@@ -1,6 +1,7 @@
 #!/usr/bin/bash
 
-for MODEL in $(find -L -iname huggingface_checkpoint|awk -F '/' '{print $3}'|sort -u)
+#for MODEL in $(find -L -iname huggingface_checkpoint|awk -F '/' '{print $3}'|sort -u)
+for MODEL in "version_26" "version_30"
 do
 	echo "Run predictions with ${MODEL}"
 	docker run --rm -ti \
@@ -8,6 +9,7 @@ do
 	    -v ${PWD}/msmarco-dev/:/input-data:ro \
 	    -v ${PWD}/output-runs/${MODEL}:/runs \
 	    -v ${PWD}/lightning_logs/${MODEL}/huggingface_checkpoint/:/model \
+	    -e CUDA_VISIBLE_DEVICES=2 \
 	    -e MODEL=/model \
 	    -e inputDataset=/input-data \
 	    -e outputDir=/runs \

### 2024-06-26 code/train-cross-encoder-bm25-cat-early-stopping-ms-marco-TinyBERT-L-2.py
feat: training for ms-marco-TinyBER-L-2

@@ -1,0 +1,179 @@
+"""
+This code is copied from https://github.com/arian-askari/injecting_bm25_score_bert_reranker and only adapted to run in a local slurm setup. I.e., data mounted to different locations.
+"""
+from torch.utils.data import DataLoader
+from sentence_transformers import LoggingHandler, util
+
+from sentence_transformers import InputExample
+import logging
+from datetime import datetime
+import gzip
+import os
+import tarfile
+import tqdm
+import torch
+import json
+
+# is included in sentence_transformers.cross_encoder.evaluation
+from CERerankingEvaluator_bm25cat import CERerankingEvaluator
+from CrossEncoderEarlyStopping import CrossEncoder
+
+# Just some code to print debug information to stdout
+logging.basicConfig(format='%(asctime)s - %(message)s',
+                    datefmt='%Y-%m-%d %H:%M:%S',
+                    level=logging.INFO,
+                    handlers=[LoggingHandler()])
+# /print debug information to stdout
+
+# We make a directory for storing the MS Marco dataset
+data_folder = '/mnt/ceph/storage/data-in-progress/data-research/web-search/RENEUIR-24/training-data-bm25-cat/'
+injection_folder = data_folder + "/injection_scores/"
+os.makedirs(injection_folder, exist_ok=True)
+
+# We download injection scores
+
+train_scores_path = os.path.join(injection_folder, '1_bm25_scores_train_triples_small.json')
+
+validation_scores_path = os.path.join(injection_folder, '5_bm25_scores_train-eval_triples.json')
+
+# Loading injection scores and applying normalization (global min-max in the paper)
+global_min_bm25 = 0
+global_max_bm25 = 50
+scores_path = injection_folder + "1_bm25_scores_train_triples_small.json"
+scores = json.loads(open(scores_path, "r").read())
+for qid in tqdm.tqdm(scores.keys(), desc="reading scores...{}".format(scores_path)):
+    for did, score in scores[qid].items():
+        normalized_score = (score - global_min_bm25) / (global_max_bm25 - global_min_bm25)
+        normalized_score = int(normalized_score * 100)
+        scores[qid][did] = normalized_score
+
+validation_scores_path = injection_folder + "/5_bm25_scores_train-eval_triples.json"
[…]

### 2024-06-26 code/train-cross-encoder-bm25-cat-ms-marco-TinyBERT-L-2.py

@@ -1,0 +1,175 @@
+"""
+This code is copied from https://github.com/arian-askari/injecting_bm25_score_bert_reranker and only adapted to run in a local slurm setup. I.e., data mounted to different locations.
+"""
+from torch.utils.data import DataLoader
+from sentence_transformers import LoggingHandler, util
+from sentence_transformers.cross_encoder import CrossEncoder
+
+from sentence_transformers import InputExample
+import logging
+from datetime import datetime
+import gzip
+import os
+import tarfile
+import tqdm
+import torch
+import json
+
+from CERerankingEvaluator_bm25cat import CERerankingEvaluator
+#### Just some code to print debug information to stdout
+logging.basicConfig(format='%(asctime)s - %(message)s',
+                    datefmt='%Y-%m-%d %H:%M:%S',
+                    level=logging.INFO,
+                    handlers=[LoggingHandler()])
+#### /print debug information to stdout
+
+### We make a directory for storing the MS Marco dataset
+data_folder = '/mnt/ceph/storage/data-in-progress/data-research/web-search/RENEUIR-24/training-data-bm25-cat/'
+injection_folder = data_folder + "/injection_scores/"
+os.makedirs(injection_folder, exist_ok=True)
+
+# We download injection scores
+
+train_scores_path = os.path.join(injection_folder, '1_bm25_scores_train_triples_small.json')
+
+validation_scores_path = os.path.join(injection_folder, '5_bm25_scores_train-eval_triples.json')
+
+# Loading injection scores and applying normalization (global min-max in the paper)
+global_min_bm25 = 0
+global_max_bm25 = 50
+scores_path = injection_folder + "1_bm25_scores_train_triples_small.json"
+scores = json.loads(open(scores_path, "r").read())
+for qid in tqdm.tqdm(scores.keys(), desc = "reading scores...{}".format(scores_path)):
+  for did, score in scores[qid].items():
+    normalized_score = (score - global_min_bm25) / (global_max_bm25 - global_min_bm25)
+    normalized_score = int(normalized_score * 100)
+    scores[qid][did] = normalized_score
+
+validation_scores_path = injection_folder + "/5_bm25_scores_train-eval_triples.json"
+scores_validation = json.loads(open(validation_scores_path, "r").read())
[…]

### 2024-06-26 code/training-slurm.sh

@@ -4,7 +4,7 @@
 #SBATCH --output=slurm-output/ir_project_training.%j.out
 #SBATCH --error=slurm-output/ir_project_training.%j.err
 #SBATCH --container-image=mam10eks/reneuir-tinybert:0.0.1
-#SBATCH --array=0-5
+#SBATCH --array=0-4
 #SBATCH --mem=60G
 #SBATCH --cpus-per-task=4
 #SBATCH --time=16:00:00
@@ -20,4 +20,5 @@ echo $SLURM_JOB_NODELIST
 cd $PWD/RENEUIR-24/code
 export PYTHONUNBUFFERED=TRUE
 echo "Run task: ${SLURM_ARRAY_TASK_ID}"
-python3 train-cross-encoder-bm25-cat.py
+python3 train-cross-encoder-bm25-cat-ms-marco-TinyBERT-L-2.py
+# python3 train-cross-encoder-bm25-cat-early-stopping-ms-marco-TinyBERT-L-2.py

### 2024-06-28 code/lightning-ir/rerank-with-model.sh
add models

@@ -2,9 +2,9 @@
 
 lightning-ir re_rank \
 	--config ${CONFIG_DIR}/tinybert-inference.yaml \
-	--data.inference_datasets.init_args.run_path ${inputDataset}/rerank.jsonl.gz \
-	--trainer.callbacks.init_args.save_dir ${outputDir}/ \
+	--data.inference_datasets.init_args.run_path ${TIRA_INPUT_DATASET}/rerank.jsonl.gz \
+	--trainer.callbacks.init_args.save_dir ${TIRA_OUTPUT_DIR}/ \
 	--model.init_args.model_name_or_path ${MODEL}
 
-mv ${outputDir}/rerank.run ${outputDir}/run.txt
+mv ${TIRA_OUTPUT_DIR}/rerank.run ${TIRA_OUTPUT_DIR}/run.txt
 

### 2024-06-28 code/run-notebook.py

@@ -1,0 +1,26 @@
+#!/usr/bin/env python3
+import argparse
+import subprocess
+import sys
+import os
+
+def parse_args():
+    parser = argparse.ArgumentParser(description='')
+
+    parser.add_argument('--notebook', type=str, help='The notebook to execute.', required=True)
+    parser.add_argument('--chdir', type=str, help='Change the directory before executing the notebook to allow for relative imports.', required=False, default=None)
+
+    return parser.parse_args()
+
+
+def main(args):
+    if args.chdir:
+        print(f'Change directory to allow relative imports to "{args.chdir}".', flush=True)
+        os.chdir(args.chdir)
+
+    command = f'runnb --allow-not-trusted {args.notebook}'
+    subprocess.check_call(command, shell=True, stdout=sys.stdout, stderr=subprocess.STDOUT)
+
+
+if __name__ == '__main__':
+    main(parse_args())

### 2024-06-28 models/build-all.sh

@@ -1,0 +1,12 @@
+#!/usr/bin/bash -e
+
+docker build -t tiny-bert-ranker -f code/Dockerfile.tinybert --build-arg MODEL_NAME=webis/tiny-bert-ranker .
+docker build -t tiny-bert-ranker-l-2 -f code/Dockerfile.tinybert --build-arg MODEL_NAME=cross-encoder/ms-marco-TinyBERT-L-2 .
+
+docker build -t tiny-bert-ranker-bm25 -f code/Dockerfile.tinybertcatbm25  --build-arg MODEL_NAME=webis/tiny-bert-ranker-bm25 .
+docker build -t tiny-bert-ranker-l2-bm25 -f code/Dockerfile.tinybertcatbm25  --build-arg MODEL_NAME=webis/tiny-bert-ranker-l2-bm25 .
+
+
+docker build -t tiny-bert-ranker-distillation -f code/lightning-ir/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-distillation .
+docker build -t tiny-bert-ranker-l-2-distillation -f code/lightning-ir/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-l-2-distillation .
+

### 2024-06-28 build/build-all.sh
prepare clean up

@@ -3,8 +3,8 @@
 docker build -t tiny-bert-ranker -f code/Dockerfile.tinybert --build-arg MODEL_NAME=webis/tiny-bert-ranker .
 docker build -t tiny-bert-ranker-l-2 -f code/Dockerfile.tinybert --build-arg MODEL_NAME=cross-encoder/ms-marco-TinyBERT-L-2 .
 
-docker build -t tiny-bert-ranker-bm25 -f code/Dockerfile.tinybertcatbm25  --build-arg MODEL_NAME=webis/tiny-bert-ranker-bm25 .
-docker build -t tiny-bert-ranker-l2-bm25 -f code/Dockerfile.tinybertcatbm25  --build-arg MODEL_NAME=webis/tiny-bert-ranker-l2-bm25 .
+docker build -t tiny-bert-ranker-bm25 -f tiny-bert-ranker-bm25/Dockerfile  --build-arg MODEL_NAME=webis/tiny-bert-ranker-bm25 .
+docker build -t tiny-bert-ranker-l2-bm25 -f tiny-bert-ranker-bm25/Dockerfile  --build-arg MODEL_NAME=webis/tiny-bert-ranker-l2-bm25 .
 
 
 docker build -t tiny-bert-ranker-distillation -f code/lightning-ir/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-distillation .

### 2024-06-28 build/build-all.sh
clean up

@@ -1,7 +1,7 @@
 #!/usr/bin/bash -e
 
-docker build -t tiny-bert-ranker -f code/Dockerfile.tinybert --build-arg MODEL_NAME=webis/tiny-bert-ranker .
-docker build -t tiny-bert-ranker-l-2 -f code/Dockerfile.tinybert --build-arg MODEL_NAME=cross-encoder/ms-marco-TinyBERT-L-2 .
+docker build -t tiny-bert-ranker -f tiny-bert-ranker/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker .
+docker build -t tiny-bert-ranker-l-2 -f tiny-bert-ranker/Dockerfile --build-arg MODEL_NAME=cross-encoder/ms-marco-TinyBERT-L-2 .
 
 docker build -t tiny-bert-ranker-bm25 -f tiny-bert-ranker-bm25/Dockerfile  --build-arg MODEL_NAME=webis/tiny-bert-ranker-bm25 .
 docker build -t tiny-bert-ranker-l2-bm25 -f tiny-bert-ranker-bm25/Dockerfile  --build-arg MODEL_NAME=webis/tiny-bert-ranker-l2-bm25 .

### 2024-06-28 build/build-all.sh
refactor

@@ -6,7 +6,6 @@ docker build -t tiny-bert-ranker-l-2 -f tiny-bert-ranker/Dockerfile --build-arg 
 docker build -t tiny-bert-ranker-bm25 -f tiny-bert-ranker-bm25/Dockerfile  --build-arg MODEL_NAME=webis/tiny-bert-ranker-bm25 .
 docker build -t tiny-bert-ranker-l2-bm25 -f tiny-bert-ranker-bm25/Dockerfile  --build-arg MODEL_NAME=webis/tiny-bert-ranker-l2-bm25 .
 
-
-docker build -t tiny-bert-ranker-distillation -f code/lightning-ir/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-distillation .
-docker build -t tiny-bert-ranker-l-2-distillation -f code/lightning-ir/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-l-2-distillation .
+docker build -t tiny-bert-ranker-distillation -f tiny-bert-ranker-distillation/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-distillation .
+docker build -t tiny-bert-ranker-l-2-distillation -f tiny-bert-ranker-distillation/Dockerfile --build-arg MODEL_NAME=webis/tiny-bert-ranker-l-2-distillation .
 

### 2024-06-28 tiny-bert-ranker/run-notebook.py
simplify entrypoint

@@ -3,6 +3,7 @@ import argparse
 import subprocess
 import sys
 import os
+from huggingface_hub import snapshot_download
 
 def parse_args():
     parser = argparse.ArgumentParser(description='')
@@ -18,6 +19,7 @@ def main(args):
         print(f'Change directory to allow relative imports to "{args.chdir}".', flush=True)
         os.chdir(args.chdir)
 
+    os.environ['MODEL'] = snapshot_download(os.environ['MODEL'])
     command = f'runnb --allow-not-trusted {args.notebook}'
     subprocess.check_call(command, shell=True, stdout=sys.stdout, stderr=subprocess.STDOUT)
 
